---
title: "TEMPO qPCR krill - Analysis"
author: "Leonie Suter, Ben Raymond, Martin Cox, Simon Wotherspoon"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    fig_caption: yes
    number_sections: yes
    toc: yes
    warning: no
  word_document:
    toc: yes
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
save_figs <- FALSE ## change to TRUE to save each fig as png file

```

```{r read-libraries}
library(SOmap) ## install via remotes::install_github("AustralianAntarcticDivision/SOmap") if needed
library(ggplot2)
library(tidyr)
library(orsifronts)
library(dplyr)
library(drc)
library(stringr)
library(ggnewscale)
library(suncalc)
library(ncdf4)
library(sf)
library(units)
library(ggrepel)
library(cowplot)
library(scatterpie)
library(geosphere)
library(PieGlyph)
library(eulerr)
library(visreg)
library(mgcv)
library(colorspace)
library(emmeans)
requireNamespace("gratia")

```

# Figure 1: overview map

## Overview inset

```{r overview-inset}
ovw.coord <- data.frame(Latitude = c(-60.1, -60, -60, -60), Longitude = c(-112, -22, 68, 158))

overview <- SOmap_auto(x = ovw.coord$Longitude, y = ovw.coord$Latitude, gratlat = c(-80, -70, -60, -50), graticules = TRUE,  input_points = FALSE, input_lines = FALSE)
myoverview <- SOgg(overview)
my_overview <- plot(myoverview)

rectangle.coord <- data.frame(Latitude = c(-60.5, -60.5, -68.2, -68.2, -60.5), Longitude = c(55, 81, 85.5, 50.5, 55))
rectangle.coord[c("Long.proj", "Lat.proj")] <- SOproj(cbind(rectangle.coord$Longitude, rectangle.coord$Latitude),  target = SOcrs())


my_overview <-  my_overview + binned_scale(name = "Depth (m)", aesthetics = "fill", scale_name = "stepsn",
               ##palette = function(x) c("#54A3D1", "#7DC9F0", "#AFDAFD", "#C4E5F4", "#D7F0FF"),#, "#EBF3F5"),
               palette = function(x) c("#2D7FAC", "#60ADD4", "#AFDAFD", "#C4E5F4", "#D7F0FF", "grey90"),#, "#EBF3F5"),
               breaks = c(-6000, -4000, -3000, -2000, -1000, 0, 9999), na.value = "grey90",
               labels = function(z) abs(z), ## remove - sign from labels
               limits = c(-6000, 4000), show.limits = TRUE, guide = "colorsteps")


overview.rectangle <-  my_overview +
  geom_path(data = rectangle.coord, aes(x=Long.proj, y=Lat.proj), lwd = 1.5) +
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

```

## Base map

```{r base-map}
eDNA <- read.csv("data/krill.eDNA.data.for.figures.csv")

eDNA$CTD.depth <- as.factor(eDNA$CTD.depth )

eDNA.CTDs <- droplevels(eDNA[eDNA$CTD.depth %in% c("top", "bottom"), ])

myplot <- SOmap_auto(c(max(eDNA.CTDs$Longitude), min(eDNA.CTDs$Longitude)-3, eDNA.CTDs$Longitude),
                     c(max(eDNA.CTDs$Latitude) + 1.8, min(eDNA.CTDs$Latitude), eDNA.CTDs$Latitude),
                     input_points = FALSE, input_lines = FALSE, fronts = TRUE)

myplotgg <- SOgg(myplot) ## creates a SOmap_gg object

## use ADD coastline, because the SOmap-bundled one is not visually consistent at this scale
cx <- readRDS("data/ADD_coastline.rds")
## note, that was created from the original ADD gpkg downloaded from BAS with:
##   cx <- sf::st_read("data/add_coastline_high_res_polygon_v7_9.gpkg")
##   cx <- SOproj(cx, target = SOcrs()) ## reproject
##   cx <- sf::st_crop(cx, sf::st_bbox(myplotgg$coastline[[1]]$plotargs$data) * c(1.2, 1.2, 1.2, 0.8)) ## crop but with extra margin
##   saveRDS(cx, "data/ADD_coastline.rds")

cx <- SOproj(cx, target = SOcrs()) ## reproject
cx <- sf::st_crop(cx, sf::st_bbox(myplotgg$coastline[[1]]$plotargs$data)) ## and re-trim

myplotgg$coastline <- SO_plotter(plotfun = "ggplot2::geom_sf",
                                 plotargs = list(data = cx[cx$surface == "land", ], fill = "#EBEBEB", col = "black", linewidth = 0.25, inherit.aes = FALSE))
myplotgg$ice <- SO_plotter(plotfun = "ggplot2::geom_sf",
                           plotargs = list(data = cx[cx$surface != "land", ], fill = "#F4F4F4", col = "black", linewidth = 0.25, inherit.aes = FALSE))

## other tweaks
myplotgg$graticule[[1]]$plotargs$linewidth <- 0.25

my_ggplot <- plot(myplotgg) ## creates a ggplot object

## add discretized (binned) scale so that bathymetry is only coloured by broad depth ranges
my_ggplot <-  my_ggplot + binned_scale(name = "Depth (m)", aesthetics = "fill", scale_name = "stepsn",
                                       palette = function(x) c("#2D7FAC", "#60ADD4", "#AFDAFD", "#C4E5F4", "#D7F0FF"),
                                       breaks = c(-6000, -4000, -3000, -2000, -1000, 0, 9999), na.value = "blue",
                                       labels = function(z) abs(z), ## remove - sign from labels
                                       limits = c(-6000, 0), show.limits = TRUE, guide = "colorsteps")


eDNA[c("Long.proj", "Lat.proj")] <- SOproj(cbind(eDNA$Longitude, eDNA$Latitude),  target = SOcrs())

## stations
Davis.station <- data.frame(Latitude = -68.5762, Longitude = 77.9696)
Mawson.station <- data.frame(Latitude = -67.6027, Longitude = 62.8730)
Davis.station[c("Long.proj", "Lat.proj")] <- SOproj(cbind(Davis.station$Longitude, Davis.station$Latitude),  target = SOcrs())
Mawson.station[c("Long.proj", "Lat.proj")] <- SOproj(cbind(Mawson.station$Longitude, Mawson.station$Latitude),  target = SOcrs())

## add TEMPO fronts
TEMPO.fronts <- read.csv("data/TEMPO_FRONTS_for_plotting.csv")
TEMPO.fronts[, 1:5] <- sapply(TEMPO.fronts[, 1:5], as.numeric)

## Project each front separately:
ASF.TEMPO <- as.data.frame(SOproj(TEMPO.fronts$Transect..oE., -TEMPO.fronts$ASF..oS., target = SOcrs()))[, 1:2]
ASF.N.TEMPO <- as.data.frame(SOproj(TEMPO.fronts$Transect..oE.[c(2:4, 6:7)], -TEMPO.fronts$ASF.N..oS.[c(2:4, 6:7)], target = SOcrs()))[, 1:2]
SB.TEMPO <- as.data.frame(SOproj(TEMPO.fronts$Transect..oE., -TEMPO.fronts$SBdy..oS., target = SOcrs()))[, 1:2]
SACCF.TEMPO <- as.data.frame(SOproj(TEMPO.fronts$Transect..oE., -TEMPO.fronts$SACCF..oS., target = SOcrs()))[, 1:2]

## generate smooth data frames
spline_ASF.TEMPO <- as.data.frame(spline(ASF.TEMPO$x, ASF.TEMPO$y))
spline_ASF.N.TEMPO <- as.data.frame(spline(ASF.N.TEMPO$x, ASF.N.TEMPO$y))
spline_SB.TEMPO <- as.data.frame(spline(SB.TEMPO$x, SB.TEMPO$y))
spline_SACCF.TEMPO <- as.data.frame(spline(SACCF.TEMPO$x, SACCF.TEMPO$y))

transect.labels <- data.frame(name = c(1:6), lat = c(rep(-61.6,4), rep(-62.6,2)), lon = c(55, 60, 65, 70, 75, 80))
transect.labels[c("Long.proj", "Lat.proj")] <- SOproj(cbind(transect.labels$lon, transect.labels$lat),  target = SOcrs())

## transect start and end times
transect_start_end <- readRDS("data/acoustic.data.files/tempo_transect_times.rds")
## helper function
transect_from_datetime <- function(dt) {
    out <- rep(NA_integer_, length(dt))
    for (i in seq_len(nrow(transect_start_end))) {
        out[which(dt >= transect_start_end$start_time_utc[i] & dt <= transect_start_end$end_time_utc[i])] <- transect_start_end$transect[i]
    }
    out
}
## underway data
ux <- data.table::fread("data/acoustic.data.files/in2021_v01uwy1min.csv", data.table = FALSE)
ux <- ux %>% dplyr::rename(longitude = "longitude(degree_east)", latitude = "latitude(degree_north)") %>%
    mutate(date_time = lubridate::dmy_hms(paste(.data$date, .data$time)))
ux$transect <- transect_from_datetime(ux$date_time)
ux[c("Long.proj", "Lat.proj")] <- SOproj(cbind(ux$longitude, ux$latitude),  target = SOcrs())

## show ice for ends of each transect
ice_dates <- ux %>% dplyr::filter(!is.na(.data$transect)) %>% group_by(.data$transect) %>% slice_min(.data$latitude) %>% mutate(date = as.Date(.data$date_time)) %>% dplyr::select("transect", "date", "longitude", "Long.proj")
ic <- stack("data/tempo-ice.grd")
## generated with (requires a machine with raadtools installed and configured):
##    library(raadtools)
##    ic <- read_amsr2_ice(ice_dates$date)
##    ic <- raster::crop(ic, c(raster::extent(xmin = 808950, xmax = 3918643, ymin = -183688, ymax = 2418787)))
##    writeRaster(ic, filename = "data/tempo-ice.grd")

## crop each layer to the (projected) transect longitude plus/minus a bit, and extract the 15% ice contours
icl <- lapply(seq_len(nlayers(ic)), function(z) {
    out <- SOproj(ic[[z]], target = SOcrs())
    raster::rasterToContour(raster::crop(out, raster::extent(c(ice_dates$Long.proj[z] + c(-1, 1) * 100e3, extent(out)[3:4]))), levels = 15)
})

## keep the northernmost contour only and convert to data.frame
icl <- bind_rows(lapply(seq_along(icl), function(z) {
    out <- coordinates(icl[[z]])
    keep <- which.max(sapply(out[[1]], function(w) max(w[, 2]))) ## keep northern-most
    setNames(as.data.frame(out[[1]][[keep]]), c("x", "y")) %>% mutate(transect = z)
}))

## add transects to base plot with thin black lines
## this will be overlaid (in some plots) with thicker lines when the acoustics was active
my_ggplot <- my_ggplot + geom_path(data = ux %>% dplyr::filter(!is.na(.data$transect)), aes(Long.proj, Lat.proj, group = transect), colour = "black", linewidth = 0.25)

## we will add the entire line for each front, but that means we need to hold the map x- and y-limits as they are now
map_lims <- c(layer_scales(my_ggplot)$x$range$range, layer_scales(my_ggplot)$y$range$range)

my_ggplot_fronts <- my_ggplot +
    geom_line(data = spline_SACCF.TEMPO, aes(x = x, y = y), colour = "darkblue", linewidth = 0.5, linetype = "dashed") +
    geom_line(data = spline_SB.TEMPO, aes(x = x, y = y), colour = "darkblue", linewidth = 0.5, linetype = "dashed") +
    geom_path(data = icl, aes(x, y, group = transect), colour = "firebrick") +
    geom_point(data = Davis.station,aes(x=Long.proj, y=Lat.proj), size = 2, stroke = 1, shape = 16, colour = "firebrick") +
    geom_point(data = Mawson.station,aes(x=Long.proj, y=Lat.proj), size = 2, stroke = 1, shape = 16, colour = "firebrick") +
    annotate(geom = "text", x = Davis.station$Long.proj + 40000, y = Davis.station$Lat.proj, colour = "#2e3785", label = "Davis station", hjust = 0) +
    annotate(geom = "text", x = Mawson.station$Long.proj, y = Mawson.station$Lat.proj-30000, colour = "#2e3785", label = "Mawson station", hjust=0) +
    annotate(geom = "label", x = transect.labels$Long.proj, y = transect.labels$Lat.proj, colour = "black", label = transect.labels$name) +
    coord_sf(xlim = map_lims[1:2], ylim = map_lims[3:4]) ## enforce previous map limits

## some general plotting settings
age_manual_colours <- c("recent" = "#35978f", "undetermined" = "grey90", "old" ="#d73027")

```

## Add sampling

```{r add-sampling-to-map}

## acoustic data = swarms
swarms <- readRDS("data/acoustic.data.files/swarms.rds") %>% dplyr::rename(date_time = "timeStamp") %>% dplyr::arrange(.data$date_time)
swarms$transect <- as.integer(swarms$transect)
swarms$biomass <- 1e-3 * swarms$vol.den.gm3 * swarms$Length* pi* (swarms$Height_mean / 2)**2 ## kg

## and intervals
echo_intervals <- readRDS("data/acoustic.data.files/TEMPO_krill_density_extra_5_6.rds")
echo_intervals$date_time <- lubridate::ymd_hms(paste(echo_intervals$Ping_date, echo_intervals$Ping_time))
echo_intervals <- echo_intervals %>% dplyr::arrange(.data$date_time)

## transform lat long:
swarms[c("Long.proj", "Lat.proj")] <- SOproj(cbind(swarms$Lon_M, swarms$Lat_M),  target = SOcrs())
echo_intervals[c("Long.proj", "Lat.proj")] <- SOproj(cbind(echo_intervals$Lon_M, echo_intervals$Lat_M),  target = SOcrs())


## find runs of acoustic krill observations spaced fairly closely together. We will plot each run as a continuous line on the map, with breaks between lines corresponding to time gaps
temp_cols <- c("date_time", "Long.proj", "Lat.proj", "Lon_M", "Lat_M")
acoustics_effort <- echo_intervals[, temp_cols] %>% dplyr::arrange(.data$date_time)
acoustics_effort$segment <- c(0, cumsum(as.numeric(diff(acoustics_effort$date_time, units = "mins")) > 60)) + 1L ## "segment" number

acoustics.map <- my_ggplot_fronts + geom_path(data = acoustics_effort, aes(x = Long.proj, y = Lat.proj, group = segment), col = "black", linewidth = 0.75)

## add CTDs, trawls. Subdivide data into:
## - CTDs only
## - trawls only
## - CTDs and trawls

## subset data to include surface CTDs and trawls
eDNA$Sample.types <-  case_when(
    eDNA$CTD.depth == "top" & is.na(eDNA$Filtered.volume..m3..tr) ~ "CTD (eDNA and visual)",
    eDNA$CTD.depth == "top" & !is.na(eDNA$Filtered.volume..m3..tr) ~ "CTD and trawl",
    is.na(eDNA$CTD.depth) & !is.na(eDNA$Filtered.volume..m3..tr) ~ "Trawl")


eDNA.for.map <- subset(eDNA, !is.na(Sample.types))
## latitude and longitude for locations where there's only trawls
eDNA.for.map$Latitude[eDNA.for.map$Sample.types == "Trawl"] <- eDNA.for.map$net_open_lat_dec.tr[eDNA.for.map$Sample.types == "Trawl"]
eDNA.for.map$Longitude[eDNA.for.map$Sample.types == "Trawl"] <- eDNA.for.map$net_open_lon_dec.tr[eDNA.for.map$Sample.types == "Trawl"]
eDNA.for.map[c("Long.proj", "Lat.proj")] <- SOproj(cbind(eDNA.for.map$Longitude, eDNA.for.map$Latitude),  target = SOcrs())

CTD.map <- acoustics.map +
    geom_point(data = eDNA.for.map, aes(Long.proj, Lat.proj, colour = Sample.types), shape = 17, size = 2) +
    scale_colour_manual(values = c("darkgoldenrod1", "tomato1", "darkmagenta", "blue")) +
    geom_point(data = eDNA.for.map, aes(Long.proj, Lat.proj), shape = 2, size = 2) +
    geom_label_repel(data = eDNA.for.map[eDNA.for.map$trawlno.tr %in% c("T18"), ], aes(Long.proj, Lat.proj,label = trawlno.tr),
                     box.padding = unit(0.25, "lines"), point.padding = unit(0, "lines"), min.segment.length = unit(0, "lines"),
                     fill = "grey", nudge_x = -40000, nudge_y = 20000) +
    geom_label_repel(data = eDNA[eDNA$Sample == "145A", ], aes(Long.proj, Lat.proj),label = "T15",
                     box.padding = unit(0.25, "lines"), point.padding = unit(0, "lines"), min.segment.length = unit(0, "lines"), fill = "grey",
                     nudge_x = 0, nudge_y = -60000) +
    labs(colour = "Sampling activity")

## extract and remove legends
Figure1.nolegend <- CTD.map + theme(legend.position = "none")
legend.all <- get_legend(CTD.map + theme(legend.box = "horizontal"))

## assemble figure:
legend.inset <- plot_grid(legend.all, overview.rectangle, nrow = 2, rel_heights = c(0.6, 1))
Figure1 <- plot_grid(Figure1.nolegend, legend.inset, nrow = 1, rel_widths = c(1, 0.6))

## jpeg(filename = "Figure1-toedit.jpg", width = 2200*1.3, height = 1400*1.3, units = "px", quality = 100, res = 300)
Figure1
## dev.off()

```

# Figure 2

## Figure 2 A + B: eDNA amount detected, surface and seafloor

```{r Figure2A-B}
eDNA$class.strict <- factor(eDNA$class.strict, levels = c("recent", "undetermined", "old", "eDNA no krill"))
eDNA.CTDs <- droplevels(eDNA[eDNA$CTD.depth %in% c("top", "bottom"), ])

Figure2A <- my_ggplot_fronts +
    geom_point(data=eDNA.CTDs[eDNA.CTDs$CTD.depth=="top", ], aes(x=Long.proj,y=Lat.proj, size = ifelse(!is.na(L1), L1, 3), colour = (class.strict), shape = eDNA_pres)) +
    scale_shape_manual(values = c(4, 16), name = "eDNA detection") +
    geom_point(data=eDNA.CTDs[eDNA.CTDs$eDNA_pres=="eDNA present"&eDNA.CTDs$CTD.depth=="top", ],
               aes(x=Long.proj,y=Lat.proj, size = L1), shape = 1) +
    geom_point(data=eDNA.CTDs[eDNA.CTDs$eDNA_pres=="eDNA absent"&eDNA.CTDs$CTD.depth=="top", ],
               aes(x=Long.proj,y=Lat.proj), size = 2, shape = 4) +
    scale_colour_manual(values = age_manual_colours, na.translate = FALSE, name = "eDNA age") +
    scale_size(limits = c(3, 9), name = "Log(eDNA copy numbers)", breaks = c(3, 5, 7, 9)) +
    ggtitle("Surface")

Figure2B <- my_ggplot_fronts +
    geom_point(data=eDNA.CTDs[eDNA.CTDs$CTD.depth=="bottom", ], aes(x=Long.proj,y=Lat.proj, size = ifelse(!is.na(L1), L1, 3), colour = (class.strict), shape = eDNA_pres)) +
    scale_shape_manual(values = c(4, 16), name = "eDNA detection") +
    geom_point(data=eDNA.CTDs[eDNA.CTDs$eDNA_pres=="eDNA present"&eDNA.CTDs$CTD.depth=="bottom", ],
               aes(x=Long.proj,y=Lat.proj, size = L1), shape = 1) +
    geom_point(data=eDNA.CTDs[eDNA.CTDs$eDNA_pres=="eDNA absent"&eDNA.CTDs$CTD.depth=="bottom", ],
               aes(x=Long.proj,y=Lat.proj), size = 2, shape = 4) +
    scale_colour_manual(values = age_manual_colours, na.translate = FALSE, name = "eDNA age") +
    scale_size(limits = c(3, 9), name = "Log(eDNA copy numbers)", breaks = c(3, 5, 7, 9)) +
    ggtitle("Seafloor")

Figure2A.nolegend <- Figure2A + theme(legend.position = "none")
Figure2B.nolegend <- Figure2B + theme(legend.position = "none")

legend.2AB.1 <- get_legend(Figure2A +guides(fill = "none", shape = "none"))
legend.2AB.2 <- get_legend(Figure2A +guides(colour = "none", size = "none"))

Figure2AB <- plot_grid(Figure2A.nolegend, Figure2B.nolegend, legend.2AB.1, legend.2AB.2,
                      nrow = 1, labels = c("A", "B", "", ""), rel_widths = c(1, 1, 0.4,0.3))

```
### Calculate effect of sampling depth on likelihood of detection:

```{r depth-likelihood-of-detection}
## Test whether the likeihood of detecting eDNA is influenced by sampling depth:
eDNA.CTDs$eDNA_pres <- as.factor(eDNA.CTDs$eDNA_pres)
model <- glm(eDNA_pres ~ CTD.depth, data = eDNA.CTDs, family = binomial)
plot(model)
summary(model)
anova(model)

```

### eDNA abundance: surface vs seafloor

```{r eDNA-abundance-surface-seafloor}
model <- lm(L1 ~ CTD.depth, data = eDNA.CTDs[eDNA.CTDs$eDNA_pres == "eDNA present", ])
summary(model)

## Does depth of sampling affect eDNA concentration in seafloor samples?
eDNA.CTDs$Sampling.depth <- as.numeric(eDNA.CTDs$Sampling.depth)

model <- lm(L1 ~ Sampling.depth, data = eDNA.CTDs[eDNA.CTDs$eDNA_pres == "eDNA present" & eDNA.CTDs$CTD.depth =="bottom", ])
summary(model) ## --> Sampling depth does not affect eDNA concentration

## Does depth of sampling affect age estimate? Using pr.2 (likelihood of being old)
model <- lm(pr.2 ~ Sampling.depth, data = eDNA.CTDs[eDNA.CTDs$eDNA_pres == "eDNA present" & eDNA.CTDs$CTD.depth =="bottom", ])
summary(model)
anova(model) ## no

```

## Figure 2 C-D

```{r Figure-2CD}

## Same as 2AB, but for metabarcoding data with species proportion of reads and size indicating overall Euphausiid copy numbers (semi quantitative stuff)

colour.saved <- c("#965A3A", "#ff7f00", "#FFD300", "#e41a1c", "#984ea3", "#377eb8", "#4daf4a")

## Surface
read.prop.names <- c("E.crystal.read.prop", "E.frig.read.prop", "E.super.read.prop", "T.greg.read.prop", "T.mac.read.prop")

## re-calculate max and min to make nice plot
max.meta.L1 <- max(eDNA.CTDs$Meta.Euphausiids.L1, na.rm = TRUE)
min.meta.L1 <- min(eDNA.CTDs$Meta.Euphausiids.L1, na.rm = TRUE)
new.max <- 12
new.min <- 4

OldRange <- (max.meta.L1 - min.meta.L1)
NewRange <- (new.max - new.min)

eDNA.CTDs$Meta.Euphausiids.L1.newrange <- (((eDNA.CTDs$Meta.Euphausiids.L1 - min.meta.L1) * NewRange) / OldRange) + new.min

Figure2C <-  my_ggplot_fronts +
    geom_point(data = subset(eDNA.CTDs[eDNA.CTDs$CTD.depth == "top", ], krill.detection == 0), aes(x = Long.proj, y = Lat.proj), shape = 4, size = 2 ) +
    new_scale("fill") +
    geom_scatterpie(data = eDNA.CTDs[eDNA.CTDs$CTD.depth == "top", ], aes(x = Long.proj, y = Lat.proj, group = Sample, r = Meta.Euphausiids.L1.newrange*2500),
                    cols = read.prop.names, alpha = 0.8) +
    scale_fill_manual(values = c("E.crystal.read.prop" = colour.saved[1],
                                 "E.frig.read.prop" = colour.saved[2],
                                 "E.super.read.prop" = colour.saved[3],
                                 "T.greg.read.prop" = colour.saved[4],
                                 "T.mac.read.prop" = colour.saved[5]),
                      labels = c("E. crystallorophias", "E. frigida", "E. superba", "T. gregaria", "T. macrura"),
                      name = "Krill species") +
    theme(legend.text = element_text(face = "italic")) +
    ggtitle("Surface")

##Seafloor
Figure2D <-  my_ggplot_fronts + new_scale("fill") +
    geom_scatterpie(data = eDNA.CTDs[eDNA.CTDs$CTD.depth == "bottom", ], aes(x = Long.proj, y = Lat.proj, group=Sample, r = Meta.Euphausiids.L1.newrange*2500),
                    cols = read.prop.names, alpha = 0.8) +
    geom_point(data = subset(eDNA.CTDs[eDNA.CTDs$CTD.depth == "bottom", ], krill.detection == 0), aes(x = Long.proj, y = Lat.proj), shape = 4, size = 2 ) +
    scale_fill_manual(values = c("E.crystal.read.prop" = colour.saved[1],
                                 "E.frig.read.prop" = colour.saved[2],
                                 "E.super.read.prop" = colour.saved[3],
                                 "T.greg.read.prop" = colour.saved[4],
                                 "T.mac.read.prop" = colour.saved[5]),
                      labels = c("E. crystallorophias", "E. frigida", "E. superba", "T. gregaria", "T. macrura"),
                      name = "Krill species") +
    theme(legend.text = element_text(face = "italic")) +
    ggtitle("Seafloor")

Figure2C.nolegend <- Figure2C + theme(legend.position = "none")
Figure2D.nolegend <- Figure2D + theme(legend.position = "none")

legend.2CD <- get_legend(Figure2C + guides(size = "none"))

Figure2CD <- plot_grid(Figure2C.nolegend, Figure2D.nolegend, legend.2CD, nrow = 1, labels = c("C", "D", ""), rel_widths = c(1, 1, 0.7))

```
## Detection numbers

### qPCR for CTDs

```{r qPCR-detections}
## Surface samples
qPCR.surface.positive <- length(eDNA.CTDs$Sample[eDNA.CTDs$CTD.depth == "top" & eDNA.CTDs$L1 > 0 & !is.na(eDNA.CTDs$L1)])
qPCR.surface.all <- length(eDNA.CTDs$Sample[eDNA.CTDs$CTD.depth == "top"])

qPCR.surface.copymax <- max(exp(eDNA.CTDs$L1[eDNA.CTDs$CTD.depth == "top" & eDNA.CTDs$L1 > 0 & !is.na(eDNA.CTDs$L1)]))
qPCR.surface.copymin <- min(exp(eDNA.CTDs$L1[eDNA.CTDs$CTD.depth == "top" & eDNA.CTDs$L1 > 0 & !is.na(eDNA.CTDs$L1)]))
qPCR.surface.copymedian <- median(exp(eDNA.CTDs$L1[eDNA.CTDs$CTD.depth == "top" & eDNA.CTDs$L1 > 0 & !is.na(eDNA.CTDs$L1)]))

qPCR.surface.recent <- length(eDNA.CTDs$Sample[eDNA.CTDs$CTD.depth == "top" & eDNA.CTDs$class.strict == "recent" &
                                               !is.na(eDNA.CTDs$class.strict)])
qPCR.surface.old <- length(eDNA.CTDs$Sample[eDNA.CTDs$CTD.depth == "top" & eDNA.CTDs$class.strict == "old" &
                                            !is.na(eDNA.CTDs$class.strict)])
qPCR.surface.undetermined <- length(eDNA.CTDs$Sample[eDNA.CTDs$CTD.depth == "top" & eDNA.CTDs$class.strict == "undetermined" &
                                                     !is.na(eDNA.CTDs$class.strict)])

## Seafloor samples
qPCR.seafloor.positive <- length(eDNA.CTDs$Sample[eDNA.CTDs$CTD.depth == "bottom" & eDNA.CTDs$L1 > 0 & !is.na(eDNA.CTDs$L1)])
qPCR.seafloore.all <- length(eDNA.CTDs$Sample[eDNA.CTDs$CTD.depth == "bottom"])

qPCR.seafloor.copymax <- max(exp(eDNA.CTDs$L1[eDNA.CTDs$CTD.depth == "bottom" & eDNA.CTDs$L1 > 0 & !is.na(eDNA.CTDs$L1)]))
qPCR.seafloor.copymin <- min(exp(eDNA.CTDs$L1[eDNA.CTDs$CTD.depth == "bottom" & eDNA.CTDs$L1 > 0 & !is.na(eDNA.CTDs$L1)]))
qPCR.seafloor.copymedian <- median(exp(eDNA.CTDs$L1[eDNA.CTDs$CTD.depth == "bottom" & eDNA.CTDs$L1 > 0 & !is.na(eDNA.CTDs$L1)]))

qPCR.seafloor.recent <- length(eDNA.CTDs$Sample[eDNA.CTDs$CTD.depth == "bottom" & eDNA.CTDs$class.strict == "recent" &
                                                !is.na(eDNA.CTDs$class.strict)])
qPCR.seafloor.old <- length(eDNA.CTDs$Sample[eDNA.CTDs$CTD.depth == "bottom" & eDNA.CTDs$class.strict == "old" &
                                             !is.na(eDNA.CTDs$class.strict)])
qPCR.seafloor.undetermined <- length(eDNA.CTDs$Sample[eDNA.CTDs$CTD.depth == "bottom" & eDNA.CTDs$class.strict == "undetermined" &
                                                      !is.na(eDNA.CTDs$class.strict)])

## Check sampling depths:
eDNA.CTDs$Sampling.depth <- as.numeric(eDNA.CTDs$Sampling.depth)
eDNA.CTDs[order(eDNA.CTDs$Sampling.depth), ]

## Copy number histogram
depth_names <- c("bottom" = "Seafloor", "top" = "Surface")

Supplementary.Figure.S2 <- ggplot(droplevels(eDNA.CTDs[eDNA.CTDs$CTD.depth %in% c("top", "bottom")]), aes(x=exp(L1), fill=class.strict)) +
    geom_histogram(colour = "black") +
    scale_fill_manual(values = age_manual_colours) +
    facet_grid(.~CTD.depth, labeller= labeller(CTD.depth = depth_names)) +
    labs(x="Short marker, copy per sample", y = "Count", fill = "eDNA age")

if (save_figs) png(filename = "Supplementary.Figure.S2.png", width = 3600, height = 2000, res = 300)
print(Supplementary.Figure.S2)
if (save_figs) dev.off()

```

### Metabarcoding

```{r detections-metabarcoding}
## Surface samples
metab.surface.E.sup <- length(eDNA.CTDs$Sample[eDNA.CTDs$CTD.depth=="top" & eDNA.CTDs$Euphausia.superba > 100 &
                                               !is.na(eDNA.CTDs$Euphausia.superba)])

metab.surface.T.mac <- length(eDNA.CTDs$Sample[eDNA.CTDs$CTD.depth=="top" & eDNA.CTDs$Thysanoessa.macrura > 100 &
                                               !is.na(eDNA.CTDs$Thysanoessa.macrura)])

metab.surface.E.frig <- length(eDNA.CTDs$Sample[eDNA.CTDs$CTD.depth=="top" & eDNA.CTDs$Euphausia.frigida > 100 &
                                                !is.na(eDNA.CTDs$Euphausia.frigida)])

metab.surface.T.gre <- length(eDNA.CTDs$Sample[eDNA.CTDs$CTD.depth=="top" & eDNA.CTDs$Thysanoessa.gregaria > 100 &
                                               !is.na(eDNA.CTDs$Thysanoessa.gregaria)])

metab.surface.E.cry <- length(eDNA.CTDs$Sample[eDNA.CTDs$CTD.depth=="top" & eDNA.CTDs$Euphausia.crystallorophias > 100 &
                                               !is.na(eDNA.CTDs$Euphausia.crystallorophias)])

## Seafloor samples
metab.seafloor.E.sup <- length(eDNA.CTDs$Sample[eDNA.CTDs$CTD.depth=="bottom" & eDNA.CTDs$Euphausia.superba > 100 &
                                                !is.na(eDNA.CTDs$Euphausia.superba)])

metab.seafloor.T.mac <- length(eDNA.CTDs$Sample[eDNA.CTDs$CTD.depth=="bottom" & eDNA.CTDs$Thysanoessa.macrura > 100 &
                                                !is.na(eDNA.CTDs$Thysanoessa.macrura)])

metab.seafloor.E.frig <- length(eDNA.CTDs$Sample[eDNA.CTDs$CTD.depth=="bottom" & eDNA.CTDs$Euphausia.frigida > 100 &
                                                 !is.na(eDNA.CTDs$Euphausia.frigida)])

metab.seafloor.T.gre <- length(eDNA.CTDs$Sample[eDNA.CTDs$CTD.depth=="bottom" & eDNA.CTDs$Thysanoessa.gregaria > 100 &
                                                !is.na(eDNA.CTDs$Thysanoessa.gregaria)])

metab.seafloor.E.cry <- length(eDNA.CTDs$Sample[eDNA.CTDs$CTD.depth=="bottom" & eDNA.CTDs$Euphausia.crystallorophias > 100 &
                                                !is.na(eDNA.CTDs$Euphausia.crystallorophias)])

```

## Figure 2 E-F

### Calculate sample distances

```{r trawl-sample-distances}
## TT15
## The swarm extends from sample 145A to 146A, and the following samples move away from it. Calculate a line for the swarm extent from 145A to 146A, and then calculate the distance of subsequent points to that line.
samples.TT15 <- eDNA$Sample[eDNA$Sampling.type == "TT 15" & !is.na(eDNA$Sampling.type == "TT 15")]
line.15 <- cbind(eDNA$Longitude[eDNA$Sample %in% samples.TT15[1:2]], eDNA$Latitude[eDNA$Sample %in% samples.TT15[1:2]])
pnts.15 <- cbind(eDNA$Longitude[eDNA$Sample %in% samples.TT15[3:6]], eDNA$Latitude[eDNA$Sample %in% samples.TT15[3:6]])
distance.15 <- dist2Line(pnts.15, line.15, distfun = distGeo)
eDNA$dist.from.swarm <- NA

## Set distance from swarm for samples collected in swarm to 0:
eDNA$dist.from.swarm[eDNA$Sample %in% samples.TT15[1:2]] <- 0
eDNA$dist.from.swarm[eDNA$Sample %in% samples.TT15[3:6]] <- distance.15[, 1]

## T18: Same approach, much more convoluted ship's track though
samples.TT18 <- c("161A","156A", "157A", "158A", "159A", "155A")

line.18 <- rbind(c(eDNA$Longitude[eDNA$Sample %in% samples.TT18[1]], eDNA$Latitude[eDNA$Sample %in% samples.TT18[1]]),
                 c(eDNA$Longitude[eDNA$Sample %in% samples.TT18[2]], eDNA$Latitude[eDNA$Sample %in% samples.TT18[2]]))

pnts.18 <- rbind(c(eDNA$Longitude[eDNA$Sample %in% samples.TT18[3]], eDNA$Latitude[eDNA$Sample %in% samples.TT18[3]]),
                 c(eDNA$Longitude[eDNA$Sample %in% samples.TT18[4]], eDNA$Latitude[eDNA$Sample %in% samples.TT18[4]]),
                 c(eDNA$Longitude[eDNA$Sample %in% samples.TT18[5]], eDNA$Latitude[eDNA$Sample %in% samples.TT18[5]]),
                 c(eDNA$Longitude[eDNA$Sample %in% samples.TT18[6]], eDNA$Latitude[eDNA$Sample %in% samples.TT18[6]]))

distance.18 <- dist2Line(pnts.18, line.18, distfun = distGeo)

#Set distance from swarm for samples collected in swarm to 0:
eDNA$dist.from.swarm[eDNA$Sample %in% samples.TT18[1:2]] <- 0

## set distance of each point to the swarm line
eDNA$dist.from.swarm[eDNA$Sample %in% samples.TT18[3]] <- distance.18[1, 1]
eDNA$dist.from.swarm[eDNA$Sample %in% samples.TT18[4]] <- distance.18[2, 1]
eDNA$dist.from.swarm[eDNA$Sample %in% samples.TT18[5]] <- distance.18[3, 1]
eDNA$dist.from.swarm[eDNA$Sample %in% samples.TT18[6]] <- distance.18[4, 1]

```

### qPCR plot

```{r both-target-trawls}
TT.dist <- eDNA[(eDNA$Sampling.type =="TT 18" & !is.na(eDNA$Sampling.type =="TT 18")) | (eDNA$Sampling.type =="TT 15" &
                                                                                         !is.na(eDNA$Sampling.type =="TT 15")), ]

TT.dist$Trawl.order <- c(1:6, 6, 2:5, 1)

## sort by trawl, then trawl order
TT.dist <- TT.dist[order(TT.dist[, "Sampling.type"], TT.dist[, "Trawl.order"]), ]
trawl_labs <- c("TT 15" = "T15", "TT 18" = "T18")

model.TT.qPCR.int <- lm(L1 ~ dist.from.swarm * Sampling.type, data = TT.dist)
summary(model.TT.qPCR.int)
anova(model.TT.qPCR.int)

## no interaction between swarm and distance - simplify:
## Used for Supplementary Table S2

model.TT.qPCR <- lm(L1 ~ dist.from.swarm + Sampling.type, data = TT.dist)

## plot(model.TT.qPCR)
summary(model.TT.qPCR)
anova(model.TT.qPCR)

cols <- colorRampPalette(c("darkorchid4", "plum2"))(6)

dist.vis <- visreg(model.TT.qPCR, "dist.from.swarm", by = "Sampling.type", overlay = TRUE, partial = FALSE, rug = FALSE, plot = FALSE)

Figure2E <- ggplot(dist.vis$fit, aes(dist.from.swarm, visregFit, linetype = factor(Sampling.type), fill = factor(Sampling.type))) +
    geom_ribbon(aes(ymin = visregLwr, ymax = visregUpr), alpha = 0.5, colour = "grey50", linetype = 1, size = 0.2) +
    geom_line() +
    scale_fill_grey(start = 0.8, end = 0.8, labels = c("T15", "T18")) +
    scale_linetype_manual(values = c(1, 1)) +
    geom_point(shape = 21, fill = "white", size = 4.5, lwd = 2, data = TT.dist, aes(y = L1, x = dist.from.swarm)) +
    geom_text(data = TT.dist, aes(x = dist.from.swarm, y = L1), label = rep(c("A", "B", "C", "D", "E", "F"), 2), hjust = 0.4, size = 3, vjust = 0.4) +
    labs(x = "Distance from swarm [m]", y = "Short marker, log(copies per sample)", fill = "eDNA age") +
    theme_bw() +
    guides(colour = "none", linetype = "none", fill = "none") +
    scale_y_continuous(breaks = c(8, 10, 12, 14), limits = c(5, 14.8)) +
    facet_grid(Sampling.type ~ ., labeller = labeller(Sampling.type = trawl_labs))

Figure2E

## Calculate distance until concentration is a) maximum surface CTD eDNA detection; b) median; c) minimum; for both T15 and T18

## Intercept:
intercept.T15 <- model.TT.qPCR$coefficients[1]
intercept.T18 <- model.TT.qPCR$coefficients[1] + model.TT.qPCR$coefficients[3]

slope <- model.TT.qPCR$coefficients[2]

## formula: distance = (target concentration - intercept)/slope
## target contentrations: min, max and median of recent CTD surface detections.

surface.recent.max.L1 <- log(max(exp(eDNA.CTDs$L1[eDNA.CTDs$CTD.depth == "top" & eDNA.CTDs$L1 > 0 &
                                                  !is.na(eDNA.CTDs$L1) & eDNA.CTDs$class.strict == "recent"]))) ## 7.74
surface.recent.min.L1 <- log(min(exp(eDNA.CTDs$L1[eDNA.CTDs$CTD.depth == "top" & eDNA.CTDs$L1 > 0 &
                                                  !is.na(eDNA.CTDs$L1) & eDNA.CTDs$class.strict == "recent"]))) ## 3.24
surface.recent.median.L1 <- log(median(exp(eDNA.CTDs$L1[eDNA.CTDs$CTD.depth == "top" & eDNA.CTDs$L1 > 0 &
                                                        !is.na(eDNA.CTDs$L1) & eDNA.CTDs$class.strict == "recent"]))) ## 5.215

dist.max.T15 <- (surface.recent.max.L1 - intercept.T15) / slope ## 1367.676
dist.min.T15 <- (surface.recent.min.L1 - intercept.T15) / slope ## 2793.62
dist.median.T15 <- (surface.recent.median.L1 - intercept.T15) / slope ## 2169.131

dist.max.T18 <- (surface.recent.max.L1 - intercept.T18) / slope ## 681.4203
dist.min.T18 <- (surface.recent.min.L1 - intercept.T18) / slope ## 2107.364
dist.median.T18 <- (surface.recent.median.L1 - intercept.T18) / slope ## 1482.875

```

### Metabarcoding plot

```{r metabarcoding-target-trawls}

## Calculate copies per metabarcoding sample. As all samples contain E. superba reads, set metabarcoding E. superba copies as qPCR values (L1). Then use metabarcoding read proportions to calculate the other species's copy numbers.
## Species detected in target trawls: E. superba, E. frigida, E. crystallorophias, T. macrura

TT.dist$E.sup.meta.L1.v2 <- TT.dist$L1
TT.dist$E.sup.meta.v2 <- exp(TT.dist$E.sup.meta.L1.v2)

TT.dist$Euphausiids.total.v2 <- TT.dist$E.sup.meta.v2 / TT.dist$E.super.read.prop
TT.dist$Euphausiids.total.L1.v2 <- log(TT.dist$Euphausiids.total.v2)

## Technically the following calculations aren't necessary, as we can just plot with read proportions, but hey ...

TT.dist$E.cry.meta.v2 <- TT.dist$Euphausiids.total.v2 * TT.dist$E.crystal.read.prop
TT.dist$E.fri.meta.v2 <- TT.dist$Euphausiids.total.v2 * TT.dist$E.frig.read.prop
TT.dist$T.mac.meta.v2 <- TT.dist$Euphausiids.total.v2 * TT.dist$T.mac.read.prop

TT.dist$E.cry.meta.L1.v2 <- log(TT.dist$E.cry.meta.v2)
TT.dist$E.fri.meta.L1.v2 <- log(TT.dist$E.fri.meta.v2)
TT.dist$T.mac.meta.L1.v2 <- log(TT.dist$T.mac.meta.v2)

TT.dist$E.cry.meta.L1.v2[is.infinite(TT.dist$E.cry.meta.L1.v2)] <- 0
TT.dist$E.fri.meta.L1.v2[is.infinite(TT.dist$E.fri.meta.L1.v2)] <- 0
TT.dist$T.mac.meta.L1.v2[is.infinite(TT.dist$T.mac.meta.L1.v2)] <- 0

TT.meta.L1s <- c("E.sup.meta.L1.v2", "E.cry.meta.L1.v2", "E.fri.meta.L1.v2", "T.mac.meta.L1.v2")

Figure2F <- ggplot(data = TT.dist, aes(x = dist.from.swarm, y = Euphausiids.total.L1.v2)) +
    geom_pie_glyph(slices = read.prop.names, colour = 'black', radius = 0.3) +
    xlab("Distance from swarm [m]") +
    ylab("log(Euphausiid copies)") +
    scale_fill_manual(values = c("E.crystal.read.prop" = colour.saved[1],
                                 "E.frig.read.prop" = colour.saved[2],
                                 "E.super.read.prop" = colour.saved[3],
                                 "T.mac.read.prop" = colour.saved[5]),
                      labels = c("E. crystallorophias",  "E. frigida", "E. superba", "T. macrura"),
                      name = "Krill species") +
    scale_y_continuous(breaks=c(8,10,12,14), limits = c(5,14.8)) +
    facet_grid(Sampling.type~., labeller = labeller(Sampling.type = trawl_labs)) +
    theme_bw() +
    theme(legend.text = element_text(face = "italic"))

```

### Figure 2 EF

```{r Figure2EF}

legend.2F <- get_legend(Figure2F)
Figure2EF <- plot_grid(Figure2E, Figure2F+guides(fill= "none"), legend.2F, nrow = 1, labels = c("E", "F", ""), rel_widths = c(1,1,0.7))

```

### Combine subfigues 2 ABCDEF

```{r combine-figure-2}

Figure2 <-  plot_grid(Figure2AB, Figure2CD, Figure2EF, nrow = 3)

## save it
## jpeg(filename = "Figure2.jpg", width = 4500, height = 4500, units = "px", quality = 100, res = 300)
if (save_figs) png(filename = "Figure.png",width = 4500, height = 4500, res = 300)
print(Figure2)
if (save_figs) dev.off()

```

# Compare metabarcoding to qPCR

## Supplementary Figure S5: correlation of copy numbers

```{r correlation-of-copy-numbers}

## Comparison to L1 (short marker)
model <- lm(Meta.E.sup.L1 ~ L1, data = eDNA.CTDs)
summary(model)
anova(model) ## R^2: 0.18

eDNA.CTDs$CTD.depth <- as.factor(eDNA.CTDs$CTD.depth)

## Used in supplementary table S3
model2 <- lm(Meta.E.sup.L1 ~ L1 + CTD.depth,  data = eDNA.CTDs)
plot(model2)
summary(model2) ## R^2: 0.4
anova(model2)

AIC(model, model2) ## model2 is better fit

## visualisation with depth included

visual <- visreg(model2, "L1", by = "CTD.depth", overlay = TRUE, partial = FALSE, rug = FALSE, plot = FALSE)

Supplementary.Figure.S5 <- ggplot(visual$fit, aes(L1, visregFit, linetype = factor(CTD.depth), fill = factor(CTD.depth))) +
    geom_ribbon(aes(ymin = visregLwr, ymax = visregUpr), alpha = 0.5, colour = "grey50", linetype = 1, size = 0.2) +
    geom_line() +
    scale_fill_grey(start = 0.5, end = 0.8, labels = c("Seafloor", "Surface")) +
    labs(linetype = "Weight", fill = "Weight") +
    geom_point(data = eDNA.CTDs, aes(y = Meta.E.sup.L1, x = L1, colour = CTD.depth), size = 3) +
    geom_point(data = eDNA.CTDs, aes(y = Meta.E.sup.L1, x = L1), shape = 1, size = 3) +
    scale_colour_manual(values = c("black", "white"), labels = c("Seafloor", "Surface")) +
    labs(x = "log(qPCR copy number)", y = "log(metabarcoding copy number)", fill = "CTD sampling depth") +
    geom_abline(slope = 1, intercept = 0, colour = "red") +
    theme_bw() +
    guides(colour = "none", linetype = "none")

## jpeg("Supplementary.Figure.S5.jpg", width = 3600, height = 2000, units = "px", quality = 100, res = 300)
if (save_figs) png(filename = "Correlation.meta.qPCR.copies.png", width = 3600, height = 2000, res = 300)
print(Supplementary.Figure.S5)
if (save_figs) dev.off()

```

## Supplementary Figures S3 and S4: mismatches of detection

```{r check-mismatches}
eDNA$overlap <- case_when(
    eDNA$metag_pres == "metagenomics E.superba present" & eDNA$eDNA_pres == "eDNA present" ~ "both",
    eDNA$metag_pres == "metagenomics E.superba present" & eDNA$eDNA_pres == "eDNA absent" ~ "Metabarcoding only",
    eDNA$metag_pres == "metagenomics E.superba absent" & eDNA$eDNA_pres == "eDNA present" ~ "qPCR only",
    eDNA$metag_pres == "metagenomics E.superba absent" & eDNA$eDNA_pres == "eDNA absent" ~ "neither")

cbind(as.character(eDNA$Sample), eDNA$overlap, eDNA$metag_pres, eDNA$eDNA_pres)

qPCR.only <- length(eDNA$overlap[eDNA$overlap =="qPCR only" & !is.na(eDNA$overlap)])
meta.only <- length(eDNA$overlap[eDNA$overlap =="Metabarcoding only" & !is.na(eDNA$overlap)])
both.methods <- length(eDNA$overlap[eDNA$overlap =="both" & !is.na(eDNA$overlap)])
neither <- length(eDNA$overlap[eDNA$overlap =="neither" & !is.na(eDNA$overlap)])

## make an euler diagram

overlap.data <- c("qPCR" = qPCR.only, "Metabarcoding" = meta.only, "qPCR&Metabarcoding" = both.methods)
Supplementary.Figure.S3 <- plot(euler(overlap.data), quantities = TRUE, legend = TRUE)

## jpeg(filename = "Supplementary.Figure.S3.jpg", width = 3600, height = 1800, units = "px", quality = 100, res = 300)
if (save_figs) png(filename = "Supplementary.Figure.S3.png", width = 3600, height = 1800, res = 300)
print(Supplementary.Figure.S3)
if (save_figs) dev.off()

## Investigate the fit

Supplementary.Figure.S4A <- ggplot(eDNA[eDNA$overlap %in% c("both", "qPCR only") & !is.na(eDNA$overlap), ], aes(x = L1, fill = class.strict)) +
    geom_histogram(colour = "black") +
    scale_fill_manual(values = age_manual_colours) +
    facet_grid( . ~overlap) +
    labs(x = "Log(short marker copies)", y = "Samples", fill = "eDNA age") +
    theme_bw()

## Question: does fragmentation and eDNA quantity explain detectability for metabarcoding?

S4A.nolegend <- Supplementary.Figure.S4A + guides(fill = "none")
legend.S4A <- get_legend(Supplementary.Figure.S4A)

Supplementary.Figure.S4B <- ggplot(eDNA[eDNA$overlap %in% c("both", "Metabarcoding only") & !is.na(eDNA$overlap), ],
                                   aes(x = Meta.E.sup.L1), fill = "deepskyblue2") +
    geom_histogram(colour = "black") +
    facet_grid(. ~overlap) +
    theme_bw() +
    labs(x = expression("Log(metabarcoding " * italic(E.~superba) * " copies)"), y = "Samples")

Supplementary.Figure.S4 <- plot_grid(S4A.nolegend, legend.S4A, Supplementary.Figure.S4B, ncol = 2,
                                     labels = c("A", "", "B"), rel_widths = c(1, 0.2, 1))

##jpeg(filename = "Supplementary.Figure.S4.jpg", width = 3600, height = 3600, units = "px", quality = 100, res = 300)
if (save_figs) png(filename = "Supplementary.Figure.S4.png", width = 3600, height = 3600, res = 300)
print(Supplementary.Figure.S4)
if (save_figs) dev.off()

## Copy numbers for mismatches:

min(eDNA$Cop.Corr.R1[eDNA$overlap == "qPCR only"], na.rm = TRUE)
max(eDNA$Cop.Corr.R1[eDNA$overlap == "qPCR only"], na.rm = TRUE)

min(eDNA$Meta.E.sup.copies[eDNA$overlap == "Metabarcoding only"], na.rm = TRUE)
max(eDNA$Meta.E.sup.copies[eDNA$overlap == "Metabarcoding only"], na.rm = TRUE)

median(eDNA$Meta.E.sup.copies[eDNA$overlap %in% c("Metabarcoding only", "both")], na.rm = TRUE)

```

# Figure 3

Overview of acoustics

```{r acoust-map}
## jpeg(filename = "Figure3.jpg", width = 2200, height = 1400, units = "px", quality = 100, res = 300)
if (save_figs) png(filename = "Figure-acoustics.png", width = 2200, height = 1400, res = 300)

print(
    acoustics.map +
    geom_point(data = echo_intervals, aes(Long.proj, Lat.proj, colour = areal_biomassden_gWWm2, size = areal_biomassden_gWWm2), inherit.aes = FALSE) +
    ## enforce scales for colour and point size to match, so they are combined into one legend on the plot
    scale_colour_distiller(palette = "Oranges", transform = "sqrt", breaks = c(0, 200, 400, 600), name = "Density (gWW/m\ub2)") +
    scale_size_continuous(breaks = c(0, 200, 400, 600), transform = "sqrt", name = "Density (gWW/m\ub2)") +
    guides(color = guide_legend(), size = guide_legend()))

if (save_figs) dev.off()

```

## eDNA vs acoustic biomass

eDNA vs acoustic biomass, by distance from surface CTD stations.

```{r echo-edna1}
max_dist_from_stn <- 15 ## km

## we want to adjust the biomass for time of day
## helper function to calculate normalized time of day (relative to midnight/sunrise/noon/sunset) from clock time
stime_to_ntod <- function(lat, lon, sample_dt) {
    if (is.na(lat) || is.na(lon) || is.na(sample_dt)) return(NA_real_)
    sampling_date <- as.Date(sample_dt) ## date
    sampling_time <- lubridate::hour(sample_dt) ## UTC hour 0-24
    ref_ntod <- c(0, 0.5, 1, 1.5) ## we use 0 for midnight, 0.5 for sunrise, 1 for noon, 1.5 for sunset, 2 (same as 0) is midnight
    ## get sunrise, sunset time (slow)
    this_dl <- suncalc::getSunlightTimes(sampling_date, lat, lon)[1, 6:7] ## sunrise sunset
    this_dl <- (unlist(this_dl) %% (24 * 3600)) / 3600
    if (this_dl[1] > this_dl[2]) this_dl[1] <- this_dl[1] - 24
    ref_dl <- c((this_dl[1] + this_dl[2]) / 2 - 12, this_dl[1], (this_dl[1] + this_dl[2]) / 2, this_dl[2]) ## midnight sunrise noon sunset
    ## the sunrise/sunset times in this_dl can be outside the range 0-24 (because e.g. sunrise for date X might have happened on X-1 if our time zone tmz is offset from our longitude, which ours is)
    ## so just repeat the times +/- 24 hours so we are sure that our sunrise/set times bracket our actual sampling time
    ## and map our sampling_time to the 0-2 scale given by the sun event times, using lifar interpolation
    out <- if (!any(is.na(ref_dl))) approx(c(ref_dl - 24, ref_dl, ref_dl+24), c(ref_ntod-2, ref_ntod, ref_ntod+2), sampling_time)$y else NA_real_
    out <- out %% 2 ## back to the 0-2 range
    if (is.na(out)) 3 else out ## NA's are too far south, 24-hour light
}

## add the normalized time of day to our acoustics dataframe
echo_intervals$ntod <- sapply(seq_len(nrow(echo_intervals)),
                              function(z) stime_to_ntod(echo_intervals$Latitude[z], echo_intervals$Longitude[z], echo_intervals$date_time[z]))

## assemble acoustics interval data (biomass) as a function of distance from each eDNA sample

fig3n_data <- bind_rows(lapply(which(eDNA$CTD.depth == "top"), function(i) {
    filt_echo <- echo_intervals %>% dplyr::filter(.data$transect == eDNA$transect[i])
    if (nrow(filt_echo) < 1) return(NULL) ## no acoustics around this station
    dd <- (geosphere::distGeo(cbind(eDNA$Longitude[i], eDNA$Latitude[i]), cbind(filt_echo$Lon_M, filt_echo$Lat_M))) / 1e3 ## km
    ind <- which(dd <= max_dist_from_stn) ## within range
    eDNA[rep(i, length(ind)), ] %>% dplyr::select(-"ntod.prev") %>%
        bind_cols(filt_echo[ind, ] %>% dplyr::select(-"transect", -"Latitude", -"Longitude", -"Lat.proj", -"Long.proj"), distance = dd[ind])
}))

## relabel eDNA age (class.strict) entries
fig3n_data <- fig3n_data %>% left_join(eDNA %>% dplyr::filter(eDNA$CTD.depth == "top") %>% count(.data$class.strict), by = "class.strict") %>%
    mutate(class.strict = case_match(.data$class.strict,
                                     "eDNA no krill" ~ "eDNA: no krill",
                                     "old" ~ "eDNA: old",
                                     "recent" ~ "eDNA: recent",
                                     "undetermined" ~ "eDNA: age undetermined",
                                     .default = .data$class.strict)) %>%
    group_by(.data$class.strict) %>%
    mutate(label = as.factor(paste0(.data$class.strict, " (N = ", .data$n[1], ")"))) %>% ungroup

## threshold "presence" at the 25th percentile of the non-zero biomass values
this <- fig3n_data %>%
    mutate(present = .data$areal_biomassden_gWWm2 > quantile(fig3n_data$areal_biomassden_gWWm2[fig3n_data$areal_biomassden_gWWm2 > 0], 0.25))

## try fits of various models for comparison
fit0 <- gam(present ~ 1, data = this, family = binomial) ## intercept only
fit1 <- gam(present ~ s(ntod, bs = "cc", k = 7), data = this, family = binomial) ## time of day
fit2 <- gam(present ~ s(distance, k = 5) + s(ntod, bs = "cc", k = 7), data = this, family = binomial) ## time of day and distance
fit3 <- gam(present ~ label + s(ntod, bs = "cc", k = 7), data = this, family = binomial) ## time of day and label (eDNA age)
fit4 <- gam(present ~ label + s(distance, by = label, k = 5) + s(ntod, bs = "cc", k = 7), data = this, family = binomial) ## time of day and distance and eDNA age
AIC(fit0, fit1, fit2, fit3, fit4)

## so there is very strong evidence that adding eDNA age (`label`) to the model improves its fit but only weak evidence that distance matters

## age class and time of day relative to intercept-only:
diff(AIC(fit3, fit0)$AIC)

## adding distance to age class and ntod model, or adding distance to the ntod-only model:
diff(AIC(fit1, fit2)$AIC)
diff(AIC(fit3, fit4)$AIC)

summary(fit3)

## plot of the effect of time of day
## jpeg("Supplementary.Figure.S6.jpg", width = 2000, height = 2000, units = "px", quality = 100, res = 300)
gratia::draw(fit3, wrap = FALSE)[[1]] + theme_bw() + labs(title = "Time of day", x = NULL, caption = NULL) +
    scale_x_continuous(limits = c(0, 2), breaks = c(0, 0.5, 1, 1.5, 2), labels = c("Midnight", "Sunrise", "Noon", "Sunset", "Midnight"))
## dev.off()

## multiple comparisons
## get the predicted values (prob of presence) per age class averaged over the diel cycle

px <- as.data.frame(expand.grid(label = levels(this$label), ntod = seq(0, 2, length.out = 48))) ## 48 times per day, i.e. half-hour intervals on average
px$fitted <- predict(fit3, newdata = px, type = "response")
px %>% group_by(.data$label) %>% dplyr::summarize(min = min(.data$fitted), max = max(.data$fitted), mean = mean(.data$fitted))

pairs(emmeans(fit3, specs = c("label"), at = list(ntod = seq(0, 2, length.out = 48))))

```

# Figure 4

## Overview of visual detections

## Plots

```{r plot-visual-surface}

eDNA.CTDs$count.class[eDNA.CTDs$count.class == 0]
eDNA.CTDs$presence[eDNA.CTDs$presence == "Y"] <- "y"
eDNA.CTDs$count.class[eDNA.CTDs$count.class==5000] <- 1000

## visual_surface
Figure4A <- my_ggplot_fronts +
    geom_point(data = eDNA.CTDs[!is.na(eDNA.CTDs$presence) & eDNA.CTDs$presence == "n" & eDNA.CTDs$CTD.depth == "top", ],
               aes(x = Long.proj, y = Lat.proj), size = 2, colour = "black", shape = 4) +
    geom_point(data = eDNA.CTDs[!is.na(eDNA.CTDs$presence) & eDNA.CTDs$presence == "y" & eDNA.CTDs$CTD.depth == "top", ],
               aes(x = Long.proj, y = Lat.proj, size = count.class), shape = 16, colour = "darkgoldenrod1", alpha = 0.8) +
    geom_point(data = eDNA.CTDs[!is.na(eDNA.CTDs$presence) & eDNA.CTDs$presence == "y"& eDNA.CTDs$CTD.depth == "top", ],
               aes(x = Long.proj, y = Lat.proj, size = count.class), shape = 1, colour = "black") +
    scale_size(range = c(1.5, 5), breaks = c(10, 100, 1000), name = "Visual abundance", labels = c("low (1-10)", "medium (10-100)", "high (>100)")) +
    ggtitle("Surface")


## visual_seafloor
Figure4B <- my_ggplot_fronts +
    geom_point(data = eDNA.CTDs[!is.na(eDNA.CTDs$presence) & eDNA.CTDs$presence == "n" & eDNA.CTDs$CTD.depth == "bottom", ],
               aes(x = Long.proj, y = Lat.proj), size = 2, colour = "black", shape = 4) +
    geom_point(data = eDNA.CTDs[!is.na(eDNA.CTDs$presence) & eDNA.CTDs$presence == "y" & eDNA.CTDs$CTD.depth == "bottom", ],
               aes(x = Long.proj, y = Lat.proj, size = count.class), shape = 16, colour = "darkgoldenrod1", alpha = 0.8) +
    geom_point(data = eDNA.CTDs[!is.na(eDNA.CTDs$presence) & eDNA.CTDs$presence == "y" & eDNA.CTDs$CTD.depth == "bottom", ],
               aes(x = Long.proj, y = Lat.proj, size = count.class), shape = 1, colour = "black") +
    scale_size(range = c(1.5, 5), breaks = c(10, 100, 1000), name = "Visual abundance", labels = c("low (1-10)", "medium (10-100)", "high (>100)")) +
    ggtitle("Seafloor")

legend.4AB <- get_legend(Figure4A)

Figure4AB <- plot_grid(Figure4A + theme(legend.position = "none"),
                       Figure4B + theme(legend.position = "none"), legend.4AB, nrow = 1, labels = c("A", "B", ""), rel_widths = c(1, 1, 0.7))

## Count things:
eDNA.CTDs[!is.na(eDNA.CTDs$presence) & eDNA.CTDs$CTD.depth == "top", ] %>% count(presence == "y") ## 18/50 surface CTDs detected E. superba visually
eDNA.CTDs[!is.na(eDNA.CTDs$presence) & eDNA.CTDs$CTD.depth == "bottom", ] %>% count(presence == "y") ## 7/48 trawls detected E. superba

## jpeg("Figure4.jpg", width = 4500, height = 1500, units = "px", quality = 100, res = 300)
print(Figure4AB)
## dev.off()

```

### Calculate effect of sampling depth on likelihood of detection:

```{r depth-likelihood-of-detection-visual}
## Test whether the likelihood of detecting krill visually is influenced by sampling depth:

eDNA.CTDs$presence <- as.factor(eDNA.CTDs$presence)

model <- glm(presence ~ CTD.depth, data = eDNA.CTDs, family = binomial)
plot(model)
summary(model)
anova(model)

```

### Visual presence, eDNA presence; Supplementary Figure S7

```{r visual-eDNA-presence}

## surface samples only
surface.vis.pres.eDNA.pres <- eDNA.CTDs %>% dplyr::filter(!is.na(.data$presence) & .data$CTD.depth == "top") %>% group_by(.data$presence) %>%
    dplyr::summarize(`eDNA present` = sum(.data$class.strict != "eDNA no krill"), `eDNA absent` = sum(.data$class.strict == "eDNA no krill"))

## seafloor samples only
seafloor.vis.pres.eDNA.pres <- eDNA.CTDs %>% dplyr::filter(!is.na(.data$presence) & .data$CTD.depth == "bottom") %>% group_by(.data$presence) %>%
    dplyr::summarize(`eDNA present` = sum(.data$class.strict != "eDNA no krill"), `eDNA absent` = sum(.data$class.strict == "eDNA no krill"))

```

### Taking visual abundance into account

```{r eDNA-visual-abundance}

## Surface and seafloor data combined
## For Supplementary Table S5
## visual abundance summary
Supp.Table.S5 <- eDNA.CTDs %>% dplyr::filter(!is.na(presence)) %>% group_by(count.class) %>%
    dplyr::summarize(`eDNA recent` = sum(class.strict == "recent"),
                     `recent mean eDNA copies` = mean(Cop.Corr.R1[class.strict == "recent"]),
                     `recent SD eDNA copies` = sd(Cop.Corr.R1[class.strict == "recent"]),
                     `eDNA undetermined` = sum(class.strict == "undetermined"),
                     `undetermined mean eDNA copies` = mean(Cop.Corr.R1[class.strict == "undetermined"]),
                     `undetermined SD eDNA copies` = sd(Cop.Corr.R1[class.strict == "undetermined"]),
                     `eDNA old` = sum(class.strict == "old"),
                     `old mean eDNA copies` = mean(Cop.Corr.R1[class.strict == "old"]),
                     `old SD eDNA copies` = sd(Cop.Corr.R1[class.strict == "old"]),
                     `eDNA absent` = sum(class.strict == "eDNA no krill"))

## do visual abundance and eDNA abundance correlate?

eDNA.CTDs$log.vis <- log10(eDNA.CTDs$count.class)
eDNA.CTDs$log.vis[is.infinite(eDNA.CTDs$log.vis)] <- 0

eDNA.CTDs$vis.class <- factor(case_when(eDNA.CTDs$count.class == 0 ~ "absent",
                                        eDNA.CTDs$count.class == 10 ~ "low",
                                        eDNA.CTDs$count.class == 100 ~ "medium",
                                        eDNA.CTDs$count.class == 1000 ~ "high"), levels = c("absent", "low", "medium", "high"))

visual.present <- subset(eDNA.CTDs, !is.na(presence) & presence == "y")

visual.present$vis <- ordered(visual.present$log.vis)
visual.present$class.strict <- droplevels(visual.present$class.strict)

## if visually detected, set to 1, else 0
visual.present$visual.detected <- ifelse(visual.present$log.vis > 0, 1, 0)

## Surface only

visual.surface.present <- subset(eDNA.CTDs, !is.na(presence) & CTD.depth == "top" & presence == "y")

visual.surface.present$visual.detected <- ifelse(visual.surface.present$log.vis > 0, 1, 0)

SuppFig7A <- ggplot(data = visual.surface.present,
                    aes(x = vis.class, y = visual.detected, fill = class.strict, label = sprintf("%0.0f", Cop.Corr.R1))) +
    geom_bar(stat = "identity", colour = "grey10", size = 0.25) +
    geom_text(size = 3, position = position_stack(vjust = 0.5)) +
    scale_fill_manual(values = c(age_manual_colours, "eDNA no krill" = "grey40")) +
    theme_bw() +
    labs(x = "Visual abundance", y = "eDNA detections", fill = "eDNA age") +
    scale_y_continuous(breaks = seq(0, 10, 2), limits = c(0, 10))

visual.surface.present$class.strict <- droplevels(visual.surface.present$class.strict)

## drop eDNA age = "undetermined" and use a binomial model:

visual.surface.present1 <- visual.surface.present[visual.surface.present$class.strict != "undetermined", ]
visual.surface.present1$class.strict <- factor(visual.surface.present1$class.strict)
visual.surface.present1$vis <- factor(visual.surface.present1$log.vis)

glm.visual.surface <- glm(vis ~ L1 + class.strict, family = binomial(), data = visual.surface.present1)
summary(glm.visual.surface)
drop1(glm.visual.surface, test = "Chi")

## Seafloor only

visual.seafloor.present <- subset(eDNA.CTDs, !is.na(presence) & CTD.depth == "bottom" & presence == "y")
visual.seafloor.present$visual.detected <- ifelse(visual.seafloor.present$log.vis > 0, 1, 0)

SuppFig7B <- ggplot(data = visual.seafloor.present,
                    aes(x = vis.class, y = visual.detected, fill = class.strict, label = sprintf("%0.0f", Cop.Corr.R1))) +
                geom_bar(stat = "identity", colour = "grey10", size = 0.25) +
                geom_text(size = 3, position = position_stack(vjust = 0.5)) +
                scale_fill_manual(values = c(age_manual_colours, "eDNA no krill" ="grey40")) +
                theme_bw() +
                labs(x="Visual abundance", y = "eDNA detections", fill = "eDNA age") +
                scale_y_continuous(breaks = seq(0, 10, 2), limits = c(0, 10))


##Combine surface and seafloor plots

legend.S7AB <- get_legend(SuppFig7B)

## Combine plots
SuppFig7AB <- plot_grid(SuppFig7A + theme(legend.position = "none"), SuppFig7B + theme(legend.position = "none"), legend.S7AB, labels = c("A", "B", ""), rel_widths = c(1, 1, 0.7), nrow = 1)


## jpeg("Supplementary.Figure.S7.jpg", width = 4500, height = 1500, units = "px", quality = 100, res = 300)
if (save_figs) png(filename = "Supplementary.Figure.S7.png", width = 4500, height = 4500, res = 300)
print(SuppFig7AB)
if (save_figs) dev.off()

```

# Figure 5

## Overview trawl detections

RMT 8 trawls include adult krill, whereas RMT 1 trawls include larval krill as well as adults.

### RMT 8 trawl

```{r RMT8-trawl}
## Identify columns with RMT8 trawl data
trawl.columns <- c("Crystal..62.2..tr","E.superba.estimate.tr", "Triacantha..assume.62.2..tr", "Tmac..33.7..tr")

## calculate total catch
eDNA$RMT8.total <- rowSums(eDNA[,trawl.columns], na.rm = TRUE)

## subset data for plotting - only rows that contain RMT8 data
RMT8 <- eDNA[!is.na(eDNA$Filtered.volume..m3..tr), ]
RMT8$RMT8.total[RMT8$RMT8.total == 0] <- NA

## transform catch amount for plotting
max.RMT8 <- max(log(RMT8$RMT8.total), na.rm = TRUE)
min.RMT8 <- min(log(RMT8$RMT8.total), na.rm = TRUE)

new.max.RMT8 <- 30000
new.min.RMT8 <- 5000

OldRange.RMT8 = (max.RMT8 - min.RMT8)
NewRange.RMT8 = (new.max.RMT8 - new.min.RMT8)

RMT8$RMT8.total.newrange = (((log(RMT8$RMT8.total) - min.RMT8) * NewRange.RMT8) / OldRange.RMT8) + new.min.RMT8

## Add an Euphausiid column to match RMT1 plot - can then share legend

RMT8$Euphausiid.fake <- 0.0011

## Need to use trawl coordinates for plotting, and re-project

myplot <- SOmap_auto(c(max(eDNA.CTDs$Longitude), min(eDNA.CTDs$Longitude)-3, eDNA.CTDs$Longitude),
                     c(max(eDNA.CTDs$Latitude) + 1.8, min(eDNA.CTDs$Latitude), eDNA.CTDs$Latitude),
                     input_points = FALSE, input_lines = FALSE, fronts = TRUE)

RMT8[c("Long.proj.2", "Lat.proj.2")] <- SOproj(cbind(RMT8$net_open_lon_dec.tr, RMT8$net_open_lat_dec.tr),  target = SOcrs())

trawl.columns.2 <- c(trawl.columns, "Euphausiid.fake")

RMT8.plot.for.legend <- my_ggplot_fronts +
    new_scale("fill") +
    geom_scatterpie(data = RMT8, aes(x = Long.proj.2, y = Lat.proj.2, group = trawlno.tr, r = RMT8.total.newrange),
                    cols = trawl.columns.2, alpha = 0.8) +
    geom_point(data = subset(RMT8, is.na(RMT8.total)), aes(x = Long.proj.2, y = Lat.proj.2), shape = 4, size = 2 ) +
    scale_fill_manual(values = c("Crystal..62.2..tr" = colour.saved[1], "E.superba.estimate.tr" = colour.saved[3],
                                 "Triacantha..assume.62.2..tr" = colour.saved[6], "Tmac..33.7..tr" = colour.saved[5],
                                 "Euphausiid.fake" = colour.saved[7]),
                      labels = c("E. crystallorophias", "E. superba", "E. triacantha", "T. macrura", "other Euphausiid"), name = "Krill species") +
    theme(legend.text = element_text(face = "italic"))

legend.5ABCD <- get_legend(RMT8.plot.for.legend + theme(legend.direction = "vertical", legend.box = "horizontal"))

```

#### Figure 5A, B: RMT8 Routine and Target Trawls

```{r RMT8-regular}

RMT8.routine <- subset(RMT8, trawltype.tr == "routine")

Figure5A <-  my_ggplot_fronts + new_scale("fill") +
    geom_scatterpie(data = RMT8.routine, aes(x = Long.proj.2, y = Lat.proj.2, group = trawlno.tr, r = RMT8.total.newrange),
                    cols = trawl.columns, alpha = 0.8) +
    geom_point(data = subset(RMT8.routine, is.na(RMT8.total)), aes(x = Long.proj.2, y = Lat.proj.2), shape = 4, size = 2 ) +
    scale_fill_manual(values = c("Crystal..62.2..tr" = colour.saved[1], "E.superba.estimate.tr" = colour.saved[3],
                                 "Triacantha..assume.62.2..tr" = colour.saved[6], "Tmac..33.7..tr" = colour.saved[5]),
                      labels = c("E. crystallorophias", "E. superba", "E. triacantha", "T. macrura"), name = "Krill species") +
    theme(legend.text = element_text(face = "italic")) +
    ggtitle("RMT 8 (juveniles/adults), routine trawl")

RMT8.target <- subset(RMT8, trawltype.tr == "target")

Figure5B <-  my_ggplot_fronts + new_scale("fill") +
    geom_scatterpie(data = RMT8.target, aes(x = Long.proj.2, y = Lat.proj.2, group = trawlno.tr, r = RMT8.total.newrange),
                    cols = trawl.columns, alpha = 0.8) +
    geom_point(data = subset(RMT8.target, is.na(RMT8.total)), aes(x = Long.proj.2, y = Lat.proj.2), shape = 4, size = 2 ) +
    scale_fill_manual(values = c("Crystal..62.2..tr" = colour.saved[1],
                                 "E.superba.estimate.tr" = colour.saved[3],
                                 "Tmac..33.7..tr" = colour.saved[5]),
                      labels = c("E. crystallorophias", "E. superba", "E. triacantha", "T. macrura"), name = "Krill species") +
    theme(legend.text = element_text(face = "italic")) +
    ggtitle("RMT 8 (juveniles/adults), target trawl")

```

### RMT 1 trawl

```{r RMT1-trawl}
## Identify columns with RMT1 trawl data
trawl.columns.1 <- c("E.superba.total.tr", "T.macrura.total.tr", "Euphausiid.total.tr")
trawl.columns.larvae <- c("E.superba.calyptopsis.I.tr", "E.superba.furcilia.II.tr",
                          "E.superba.furcilia.II.1.tr", "E.superba.late.stage.furcilia.tr",
                          "T.macrura.calyptopsis.I.tr", "T.macrura.calypopsis.II.tr",
                          "T.macrura.calyptopsis.III.tr", "T.macrura.late.furcilia.tr",
                          "T.macrura.furcilia.I.tr", "T.macrura.furcilia.II.tr",
                          "T.macrura.furcilia.III.tr", "T.macrura.furcilia.IV.tr",
                          "T.macrura.furcilia.V.tr", "T.macrura.furcilia.VI.tr",
                          "Euphausiid.calyptopsis.tr" , "Euphausiid.calyptopsis.I.tr",
                          "Euphausiid.calyptopsis.II.tr", "Euphausiid.furcilia.tr",
                          "Euphausiid.furcilia.I.tr")
eDNA$E.superba.larvae <- rowSums(eDNA[,trawl.columns.larvae[1:4]])
eDNA$T.macrura.larvae <- rowSums(eDNA[,trawl.columns.larvae[5:14]])
eDNA$Euphausiid.larvae <- rowSums(eDNA[,trawl.columns.larvae[15:19]])

trawl.larvae.totals <- c("E.superba.larvae", "T.macrura.larvae", "Euphausiid.larvae")

## calculate total catch
eDNA$RMT1.total <- rowSums(eDNA[, trawl.columns.1], na.rm = TRUE)

## calculate total larvae catch
eDNA$RMT1.larvae.total <- rowSums(eDNA[, trawl.columns.larvae], na.rm = TRUE)

## subset data for plotting - only rows that contain RMT1 data
RMT1 <- eDNA[!is.na(eDNA$E.superba.tr), ]

RMT1$RMT1.total[RMT1$RMT1.total == 0] <- NA
RMT1$RMT1.larvae.total[RMT1$RMT1.larvae.total == 0] <- NA

## use the RMT8 adjustment values on RMT1, so that across the figure the values are comparable:

RMT1$RMT1.total.newrange = (((log(RMT1$RMT1.total) - min.RMT8) * NewRange.RMT8) / OldRange.RMT8) + new.min.RMT8
max.RMT1.new <- max(log(RMT1$RMT1.total.newrange), na.rm = TRUE)

# transform catch amount for plotting, larvae only
max.RMT1.larvae <- max(log(RMT1$RMT1.larvae.total), na.rm = TRUE)
min.RMT1.larvae <- min(log(RMT1$RMT1.larvae.total), na.rm = TRUE)

new.max.RMT1.larvae <- 30000
new.min.RMT1.larvae <- 5000

OldRange.RMT1.larvae = (max.RMT1.larvae - min.RMT1.larvae)
NewRange.RMT1.larvae = (new.max.RMT1.larvae - new.min.RMT1.larvae)

RMT1$RMT1.larvae.newrange = (((log(RMT1$RMT1.larvae.total) - min.RMT1.larvae) * NewRange.RMT1.larvae) / OldRange.RMT1.larvae) + new.min.RMT1.larvae

## Need to use trawl coordinates for plotting, and re-project
RMT1[c("Long.proj.2", "Lat.proj.2")] <- SOproj(cbind(RMT1$net_open_lon_dec.tr, RMT1$net_open_lat_dec.tr),  target = SOcrs())

```

#### Figure 5C,D: Plot larvae separately for routine and target trawls:

```{r routine-target-RMT1}
RMT1.routine <- subset(RMT1, trawltype.tr == "routine")
RMT1.target <- subset(RMT1, trawltype.tr == "target")

Figure5C <-  my_ggplot_fronts + new_scale("fill") +
    geom_scatterpie(data = RMT1.routine, aes(x = Long.proj.2, y = Lat.proj.2, group = trawlno.tr, r = RMT1.larvae.newrange),
                    cols = trawl.larvae.totals, alpha = 0.8) +
    scale_fill_manual(values = c("E.superba.larvae" = colour.saved[3], "T.macrura.larvae" = colour.saved[5], "Euphausiid.larvae" = colour.saved[7]),
                      labels = c("E. superba", "T. macrura", "other Euphausiids"), name = "Krill species") +
    theme(legend.text = element_text(face = "italic")) +
    geom_point(data = subset(RMT1.routine, is.na(RMT1.larvae.total)), aes(x = Long.proj.2, y = Lat.proj.2), shape = 4, size = 2, lwd = 2) +
    ggtitle("RMT 1 (larvae), routine trawl")

Figure5D <-  my_ggplot_fronts + new_scale("fill") +
    geom_scatterpie(data = RMT1.target, aes(x = Long.proj.2, y = Lat.proj.2, group=trawlno.tr, r = RMT1.larvae.newrange),
                    cols = trawl.larvae.totals, alpha = 0.8) +
    scale_fill_manual(values = c("E.superba.larvae" = colour.saved[3], "T.macrura.larvae" = colour.saved[5], "Euphausiid.larvae" = colour.saved[7]),
                      labels = c("E. superba", "T. macrura", "other Euphausiids"), name = "Krill species") +
    theme(legend.text = element_text(face = "italic")) +
    geom_point(data = subset(RMT1.target, is.na(RMT1.larvae.total)), aes(x = Long.proj.2, y = Lat.proj.2), shape = 4, size = 2, lwd = 2) +
    ggtitle("RMT 1 (larvae), target trawl")

```

### Figure 5ABCD (Target and Routine separately)

```{r figure5abcd}

Figure5ABCD.noleg <- plot_grid(Figure5A + theme(legend.position = "none"), Figure5B + theme(legend.position = "none"),
                               Figure5C + theme(legend.position = "none"), Figure5D + theme(legend.position = "none"),
                               ncol = 2, labels = c("A", "B", "C", "D"), rel_widths = c(1,1))
Figure5ABCD <- plot_grid(Figure5ABCD.noleg, legend.5ABCD, ncol = 2, rel_widths = c(2, 0.7))

```

## Count stuff

### Supplementary Table S6: RMT-8

```{r count-RMT8-detections}

## Detections

## All combined
RMT8.E.sup <- RMT8 %>% count(E.superba.estimate.tr > 0)
RMT8.E.cry <- RMT8 %>% count(Crystal..62.2..tr > 0)
RMT8.T.mac <- RMT8 %>% count(Tmac..33.7..tr > 0)
RMT8.E.tri  <- RMT8 %>% count(Triacantha..assume.62.2..tr > 0)

## Target trawl detections
RMT8.E.sup.target <- RMT8.target %>% count(E.superba.estimate.tr > 0) ## 14/15 trawls detected E. superba
RMT8.E.cry.target <- RMT8.target %>% count(Crystal..62.2..tr > 0) ## 1/15 trawls detected E. crystallorophias
RMT8.T.mac.target <- RMT8.target %>% count(Tmac..33.7..tr > 0) ## 1/15 trawls detected T. macrura
RMT8.E.tria.target <- RMT8.target %>% count(Triacantha..assume.62.2..tr > 0) ## 0/15 trawls detected E. triacantha

## Routine trawl detections
RMT8.E.sup.routine <- RMT8.routine %>% count(E.superba.estimate.tr > 0) ## 21/38 trawls detected E. superba
RMT8.E.cry.routine <- RMT8.routine %>% count(Crystal..62.2..tr > 0) ## 4/38 trawls detected E. crystallorophias
RMT8.T.mac.routine <- RMT8.routine %>% count(Tmac..33.7..tr > 0) ## 25/38 trawls detected T. macrura
RMT8.E.tri.routine <- RMT8.routine %>% count(Triacantha..assume.62.2..tr > 0) ## 8/38 trawls detected E. triacantha

## Abundances per species:
## All combined:

## E. superba
Mean.abundance.E.superba <- mean(RMT8$E.superba.estimate.tr[RMT8$E.superba.estimate.tr > 0])
Median.abundance.E.superba <- median(RMT8$E.superba.estimate.tr[RMT8$E.superba.estimate.tr > 0])
SD.abundance.E.superba <- sd(RMT8$E.superba.estimate.tr[RMT8$E.superba.estimate.tr > 0])
max.abundance.E.superba <- max(RMT8$E.superba.estimate.tr[RMT8$E.superba.estimate.tr > 0])
min.abundance.E.superba <- min(RMT8$E.superba.estimate.tr[RMT8$E.superba.estimate.tr > 0])

## T. macrura
Mean.abundance.T.macrura <- mean(RMT8$Tmac..33.7..tr[RMT8$Tmac..33.7..tr > 0])
Median.abundance.T.macrura <- median(RMT8$Tmac..33.7..tr[RMT8$Tmac..33.7..tr > 0])
SD.abundance.T.macrura <- sd(RMT8$Tmac..33.7..tr[RMT8$Tmac..33.7..tr > 0])
max.abundance.T.macrura <- max(RMT8$Tmac..33.7..tr[RMT8$Tmac..33.7..tr > 0])
min.abundance.T.macrura <- min(RMT8$Tmac..33.7..tr[RMT8$Tmac..33.7..tr > 0])

## E. crystallorophias
Mean.abundance.E.crystal <- mean(RMT8$Crystal..62.2..tr[RMT8$Crystal..62.2..tr > 0])
Median.abundance.E.crystal <- median(RMT8$Crystal..62.2..tr[RMT8$Crystal..62.2..tr > 0])
SD.abundance.E.crystal <- sd(RMT8$Crystal..62.2..tr[RMT8$Crystal..62.2..tr > 0])
max.abundance.E.crystal <- max(RMT8$Crystal..62.2..tr[RMT8$Crystal..62.2..tr > 0])
min.abundance.E.crystal <- min(RMT8$Crystal..62.2..tr[RMT8$Crystal..62.2..tr > 0])

## E. triacantha
Mean.abundance.E.triacantha <- mean(RMT8$Triacantha..assume.62.2..tr[RMT8$Triacantha..assume.62.2..tr > 0])
Median.abundance.E.triacantha <- median(RMT8$Triacantha..assume.62.2..tr[RMT8$Triacantha..assume.62.2..tr > 0])
SD.abundance.E.triacantha <- sd(RMT8$Triacantha..assume.62.2..tr[RMT8$Triacantha..assume.62.2..tr > 0])
max.abundance.E.triacantha <- max(RMT8$Triacantha..assume.62.2..tr[RMT8$Triacantha..assume.62.2..tr > 0])
min.abundance.E.triacantha <- min(RMT8$Triacantha..assume.62.2..tr[RMT8$Triacantha..assume.62.2..tr > 0])

## Combined table:
RMT8.abundances.combined <- data.frame(Species = c("Detections","Max", "Min", "Mean", "Median", "SD"),
                                       `E. superba` = c(sprintf("%0.0f", RMT8.E.sup[2, 2]),
                                                        sprintf("%0.2f", max.abundance.E.superba),
                                                        sprintf("%0.2f", min.abundance.E.superba),
                                                        sprintf("%0.2f", Mean.abundance.E.superba),
                                                        sprintf("%0.2f", Median.abundance.E.superba),
                                                        sprintf("%0.2f", SD.abundance.E.superba)),
                                       `T. macrura` = c(sprintf("%0.0f", RMT8.T.mac[2, 2]),
                                                        sprintf("%0.2f", max.abundance.T.macrura),
                                                        sprintf("%0.2f", min.abundance.T.macrura),
                                                        sprintf("%0.2f", Mean.abundance.T.macrura),
                                                        sprintf("%0.2f", Median.abundance.T.macrura),
                                                        sprintf("%0.2f", SD.abundance.T.macrura)),
                                       `E. crystallorophias` = c(sprintf("%0.0f", RMT8.E.cry[2, 2]),
                                                                 sprintf("%0.2f", max.abundance.E.crystal),
                                                                 sprintf("%0.2f", min.abundance.E.crystal),
                                                                 sprintf("%0.2f", Mean.abundance.E.crystal),
                                                                 sprintf("%0.2f", Median.abundance.E.crystal),
                                                                 sprintf("%0.2f", SD.abundance.E.crystal)),
                                       `E. triacantha` = c(sprintf("%0.0f", RMT8.E.tri[2, 2]),
                                                           sprintf("%0.2f", max.abundance.E.triacantha),
                                                           sprintf("%0.2f", min.abundance.E.triacantha),
                                                           sprintf("%0.2f", Mean.abundance.E.triacantha),
                                                           sprintf("%0.2f", Median.abundance.E.triacantha),
                                                           sprintf("%0.2f", SD.abundance.E.triacantha)))
## write.csv(RMT8.abundances.combined, "RMT8.abundances.combined.csv", row.names = FALSE)

## TARGET
## E. superba
Target.Mean.abundance.E.superba <- mean(RMT8.target$E.superba.estimate.tr[RMT8.target$E.superba.estimate.tr > 0])
Target.Median.abundance.E.superba <- median(RMT8.target$E.superba.estimate.tr[RMT8.target$E.superba.estimate.tr > 0])
Target.SD.abundance.E.superba <- sd(RMT8.target$E.superba.estimate.tr[RMT8.target$E.superba.estimate.tr > 0])
Target.max.abundance.E.superba <- max(RMT8.target$E.superba.estimate.tr[RMT8.target$E.superba.estimate.tr > 0])
Target.min.abundance.E.superba <- min(RMT8.target$E.superba.estimate.tr[RMT8.target$E.superba.estimate.tr > 0])

## T. macrura
Target.Mean.abundance.T.macrura <- mean(RMT8.target$Tmac..33.7..tr[RMT8.target$Tmac..33.7..tr > 0])
Target.Median.abundance.T.macrura <- median(RMT8.target$Tmac..33.7..tr[RMT8.target$Tmac..33.7..tr > 0])
Target.SD.abundance.T.macrura <- sd(RMT8.target$Tmac..33.7..tr[RMT8.target$Tmac..33.7..tr > 0])
Target.max.abundance.T.macrura <- max(RMT8.target$Tmac..33.7..tr[RMT8.target$Tmac..33.7..tr > 0])
Target.min.abundance.T.macrura <- min(RMT8.target$Tmac..33.7..tr[RMT8.target$Tmac..33.7..tr > 0])

## E. crystallorophias
Target.Mean.abundance.E.crystal <- mean(RMT8.target$Crystal..62.2..tr[RMT8.target$Crystal..62.2..tr > 0])
Target.Median.abundance.E.crystal <- median(RMT8.target$Crystal..62.2..tr[RMT8.target$Crystal..62.2..tr > 0])
Target.SD.abundance.E.crystal <- sd(RMT8.target$Crystal..62.2..tr[RMT8.target$Crystal..62.2..tr > 0])
Target.max.abundance.E.crystal <- max(RMT8.target$Crystal..62.2..tr[RMT8.target$Crystal..62.2..tr > 0])
Target.min.abundance.E.crystal <- min(RMT8.target$Crystal..62.2..tr[RMT8.target$Crystal..62.2..tr > 0])

## E. triacantha
Target.Mean.abundance.E.triacantha <- mean(RMT8.target$Triacantha..assume.62.2..tr[RMT8.target$Triacantha..assume.62.2..tr > 0])
Target.Median.abundance.E.triacantha <- median(RMT8.target$Triacantha..assume.62.2..tr[RMT8.target$Triacantha..assume.62.2..tr > 0])
Target.SD.abundance.E.triacantha <- sd(RMT8.target$Triacantha..assume.62.2..tr[RMT8.target$Triacantha..assume.62.2..tr > 0])
Target.max.abundance.E.triacantha <- max(RMT8.target$Triacantha..assume.62.2..tr[RMT8.target$Triacantha..assume.62.2..tr > 0])
Target.min.abundance.E.triacantha <- min(RMT8.target$Triacantha..assume.62.2..tr[RMT8.target$Triacantha..assume.62.2..tr > 0])

## Routine
## E. superba
Routine.Mean.abundance.E.superba <- mean(RMT8.routine$E.superba.estimate.tr[RMT8.routine$E.superba.estimate.tr > 0])
Routine.Median.abundance.E.superba <- median(RMT8.routine$E.superba.estimate.tr[RMT8.routine$E.superba.estimate.tr > 0])
Routine.SD.abundance.E.superba <- sd(RMT8.routine$E.superba.estimate.tr[RMT8.routine$E.superba.estimate.tr > 0])
Routine.max.abundance.E.superba <- max(RMT8.routine$E.superba.estimate.tr[RMT8.routine$E.superba.estimate.tr > 0])
Routine.min.abundance.E.superba <- min(RMT8.routine$E.superba.estimate.tr[RMT8.routine$E.superba.estimate.tr > 0])

## T. macrura
Routine.Mean.abundance.T.macrura <- mean(RMT8.routine$Tmac..33.7..tr[RMT8.routine$Tmac..33.7..tr > 0])
Routine.Median.abundance.T.macrura <- median(RMT8.routine$Tmac..33.7..tr[RMT8.routine$Tmac..33.7..tr > 0])
Routine.SD.abundance.T.macrura <- sd(RMT8.routine$Tmac..33.7..tr[RMT8.routine$Tmac..33.7..tr > 0])
Routine.max.abundance.T.macrura <- max(RMT8.routine$Tmac..33.7..tr[RMT8.routine$Tmac..33.7..tr > 0])
Routine.min.abundance.T.macrura <- min(RMT8.routine$Tmac..33.7..tr[RMT8.routine$Tmac..33.7..tr > 0])

## E. crystallorophias
Routine.Mean.abundance.E.crystal <- mean(RMT8.routine$Crystal..62.2..tr[RMT8.routine$Crystal..62.2..tr > 0])
Routine.Median.abundance.E.crystal <- median(RMT8.routine$Crystal..62.2..tr[RMT8.routine$Crystal..62.2..tr > 0])
Routine.SD.abundance.E.crystal <- sd(RMT8.routine$Crystal..62.2..tr[RMT8.routine$Crystal..62.2..tr > 0])
Routine.max.abundance.E.crystal <- max(RMT8.routine$Crystal..62.2..tr[RMT8.routine$Crystal..62.2..tr > 0])
Routine.min.abundance.E.crystal <- min(RMT8.routine$Crystal..62.2..tr[RMT8.routine$Crystal..62.2..tr > 0])

## E. triacantha
Routine.Mean.abundance.E.triacantha <- mean(RMT8.routine$Triacantha..assume.62.2..tr[RMT8.routine$Triacantha..assume.62.2..tr > 0])
Routine.Median.abundance.E.triacantha <- median(RMT8.routine$Triacantha..assume.62.2..tr[RMT8.routine$Triacantha..assume.62.2..tr > 0])
Routine.SD.abundance.E.triacantha <- sd(RMT8.routine$Triacantha..assume.62.2..tr[RMT8.routine$Triacantha..assume.62.2..tr > 0])
Routine.max.abundance.E.triacantha <- max(RMT8.routine$Triacantha..assume.62.2..tr[RMT8.routine$Triacantha..assume.62.2..tr > 0])
Routine.min.abundance.E.triacantha <- min(RMT8.routine$Triacantha..assume.62.2..tr[RMT8.routine$Triacantha..assume.62.2..tr > 0])

## Make a table:
RMT8.abundances <- data.frame(Species = c("Trawl", "Detections","Max", "Min", "Mean", "Median", "SD"),
                              `E. superba` = c("Routine (n=38)",
                                               sprintf("%0.0f", RMT8.E.sup.routine[2, 2]),
                                               sprintf("%0.2f", Routine.max.abundance.E.superba),
                                               sprintf("%0.2f", Routine.min.abundance.E.superba),
                                               sprintf("%0.2f", Routine.Mean.abundance.E.superba),
                                               sprintf("%0.2f", Routine.Median.abundance.E.superba),
                                               sprintf("%0.2f", Routine.SD.abundance.E.superba)),
                              `T. macrura` = c("Routine (n=38)",
                                               sprintf("%0.0f", RMT8.T.mac.routine[2, 2]),
                                               sprintf("%0.2f", Routine.max.abundance.T.macrura),
                                               sprintf("%0.2f", Routine.min.abundance.T.macrura),
                                               sprintf("%0.2f", Routine.Mean.abundance.T.macrura),
                                               sprintf("%0.2f", Routine.Median.abundance.T.macrura),
                                               sprintf("%0.2f", Routine.SD.abundance.T.macrura)),
                              `E. crystallorophias` = c("Routine (n=38)",
                                                        sprintf("%0.0f", RMT8.E.cry.routine[2, 2]),
                                                        sprintf("%0.2f", Routine.max.abundance.E.crystal),
                                                        sprintf("%0.2f", Routine.min.abundance.E.crystal),
                                                        sprintf("%0.2f", Routine.Mean.abundance.E.crystal),
                                                        sprintf("%0.2f", Routine.Median.abundance.E.crystal),
                                                        sprintf("%0.2f", Routine.SD.abundance.E.crystal)),
                              `E. triacantha` = c("Routine (n=38)",
                                                  sprintf("%0.0f", RMT8.E.tri.routine[2, 2]),
                                                  sprintf("%0.2f", Routine.max.abundance.E.triacantha),
                                                  sprintf("%0.2f", Routine.min.abundance.E.triacantha),
                                                  sprintf("%0.2f", Routine.Mean.abundance.E.triacantha),
                                                  sprintf("%0.2f", Routine.Median.abundance.E.triacantha),
                                                  sprintf("%0.2f", Routine.SD.abundance.E.triacantha)),
                              `E. superba` = c("Target (n=15)",
                                               sprintf("%0.0f", RMT8.E.sup.target[2, 2]),
                                               sprintf("%0.2f", Target.max.abundance.E.superba),
                                               sprintf("%0.2f", Target.min.abundance.E.superba),
                                               sprintf("%0.2f", Target.Mean.abundance.E.superba),
                                               sprintf("%0.2f", Target.Median.abundance.E.superba),
                                               sprintf("%0.2f", Target.SD.abundance.E.superba)),
                               `T. macrura` = c("Target (n=15)",
                                              sprintf("%0.0f", RMT8.T.mac.target[2, 2]),
                                              sprintf("%0.2f", Target.max.abundance.T.macrura),
                                              sprintf("%0.2f", Target.min.abundance.T.macrura),
                                              sprintf("%0.2f", Target.Mean.abundance.T.macrura),
                                              sprintf("%0.2f", Target.Median.abundance.T.macrura),
                                              sprintf("%0.2f", Target.SD.abundance.T.macrura)),
                              `E. crystallorophias` = c("Target (n=38)",
                                                        sprintf("%0.0f", RMT8.E.cry.target[2, 2]),
                                                        sprintf("%0.2f", Target.max.abundance.E.crystal),
                                                        sprintf("%0.2f", Target.min.abundance.E.crystal),
                                                        sprintf("%0.2f", Target.Mean.abundance.E.crystal),
                                                        sprintf("%0.2f", Target.Median.abundance.E.crystal),
                                                        sprintf("%0.2f", Target.SD.abundance.E.crystal)),
                              `E. triacantha` = c("Target (n=38)",
                                                  sprintf("%0.0f", RMT8.E.tria.target[2, 2]),
                                                  sprintf("%0.2f", Target.max.abundance.E.triacantha),
                                                  sprintf("%0.2f", Target.min.abundance.E.triacantha),
                                                  sprintf("%0.2f", Target.Mean.abundance.E.triacantha),
                                                  sprintf("%0.2f", Target.Median.abundance.E.triacantha),
                                                  sprintf("%0.2f", Target.SD.abundance.E.triacantha)))

## write.csv(RMT8.abundances, "RMT8.abundances.csv", row.names = FALSE)

```

### Supplementary Table S7: RMT-1

```{r count-RMT1-larval-detections}
RMT1.E.sup <- RMT1 %>% count(E.superba.larvae > 0) ## 9/48 trawls detected E. superba larvae
RMT1.T.mac <- RMT1 %>% count(T.macrura.larvae > 0) ## 29/48 trawls detected T. macrura larvae
RMT1.Eupha <- RMT1 %>% count(Euphausiid.larvae > 0) ## 16/48 trawls detected other Euphausiid larvae

Target.RMT1.E.sup <- RMT1.target %>% count(E.superba.larvae > 0) ## 9/48 trawls detected E. superba larvae
Target.RMT1.T.mac <- RMT1.target %>% count(T.macrura.larvae > 0) ## 29/48 trawls detected T. macrura larvae
Target.RMT1.Eupha <- RMT1.target %>% count(Euphausiid.larvae > 0) ## 16/48 trawls detected other Euphausiid larvae

Routine.RMT1.E.sup <- RMT1.routine %>% count(E.superba.larvae > 0) ## 9/48 trawls detected E. superba larvae
Routine.RMT1.T.mac <- RMT1.routine %>% count(T.macrura.larvae > 0) ## 29/48 trawls detected T. macrura larvae
Routine.RMT1.Eupha <- RMT1.routine %>% count(Euphausiid.larvae > 0) ## 16/48 trawls detected other Euphausiid larvae

Larvae <- c("E.superba.larvae", "T.macrura.larvae", "Euphausiid.larvae")

## E. superba
Mean.abundance.E.superba.1 <- mean(RMT1[, Larvae[1]][RMT1[, Larvae[1]] > 0]) ## 82.05593
Median.abundance.E.superba.1 <- median(RMT1[, Larvae[1]][RMT1[, Larvae[1]] > 0]) ## 12.4225
SD.abundance.E.superba.1 <- sd(RMT1[, Larvae[1]][RMT1[, Larvae[1]] > 0]) ## 138.3177
max.abundance.E.superba.1 <- max(RMT1[, Larvae[1]][RMT1[, Larvae[1]] > 0]) ## 338.5949
min.abundance.E.superba.1 <- min(RMT1[, Larvae[1]][RMT1[, Larvae[1]] > 0]) ## 0.9081856

#T. macrura
Mean.abundance.T.macrura.1 <- mean(RMT1[, Larvae[2]][RMT1[, Larvae[2]] > 0]) ## 234.1013
Median.abundance.T.macrura.1 <- median(RMT1[, Larvae[2]][RMT1[, Larvae[2]] > 0]) ## 93.05608
SD.abundance.T.macrura.1 <- sd(RMT1[, Larvae[2]][RMT1[, Larvae[2]] > 0]) ## 321.6655
max.abundance.T.macrura.1 <- max(RMT1[, Larvae[2]][RMT1[, Larvae[2]] > 0]) ## 1173.974
min.abundance.T.macrura.1 <- min(RMT1[, Larvae[2]][RMT1[, Larvae[2]] > 0]) ## 4.540928

#Euphausiids
Mean.abundance.Euphausiids <- mean(RMT1[, Larvae[3]][RMT1[, Larvae[3]] > 0]) ## 97.01558
Median.abundance.Euphausiids <- median(RMT1[, Larvae[3]][RMT1[, Larvae[3]] > 0]) ## 56.66976
SD.abundance.Euphausiids <- sd(RMT1[, Larvae[3]][RMT1[, Larvae[3]] > 0]) ## 149.8295
max.abundance.Euphausiids <- max(RMT1[, Larvae[3]][RMT1[, Larvae[3]] > 0]) ## 616.5473
min.abundance.Euphausiids <- min(RMT1[, Larvae[3]][RMT1[, Larvae[3]] > 0]) ## 1.051017

## Make a table:
RMT1.abundances.combined <- data.frame(Species = c("Detections","Max", "Min", "Mean", "Median", "SD"),
                                       `E. superba` = c(sprintf("%0.0f", RMT1.E.sup[2, 2]),
                                                        sprintf("%0.2f", max.abundance.E.superba.1),
                                                        sprintf("%0.2f", min.abundance.E.superba.1),
                                                        sprintf("%0.2f", Mean.abundance.E.superba.1),
                                                        sprintf("%0.2f", Median.abundance.E.superba.1),
                                                        sprintf("%0.2f", SD.abundance.E.superba.1)),
                                       `T. macrura` = c(sprintf("%0.0f", RMT1.T.mac[2, 2]),
                                                        sprintf("%0.2f", max.abundance.T.macrura.1),
                                                        sprintf("%0.2f", min.abundance.T.macrura.1),
                                                        sprintf("%0.2f", Mean.abundance.T.macrura.1),
                                                        sprintf("%0.2f", Median.abundance.T.macrura.1),
                                                        sprintf("%0.2f", SD.abundance.T.macrura.1)),
                                       Euphausiids = c(sprintf("%0.0f", RMT1.Eupha[2, 2]),
                                                       sprintf("%0.2f", max.abundance.Euphausiids),
                                                       sprintf("%0.2f", min.abundance.Euphausiids),
                                                       sprintf("%0.2f", Mean.abundance.Euphausiids),
                                                       sprintf("%0.2f", Median.abundance.Euphausiids),
                                                       sprintf("%0.2f", SD.abundance.Euphausiids)))

## write.csv(RMT1.abundances.combined, "RMT1.abundances.combined.csv", row.names = FALSE)

## TARGET

## E. superba
Target.Mean.abundance.E.superba.1 <- mean(RMT1.target[, Larvae[1]][RMT1.target[, Larvae[1]] > 0])
Target.Median.abundance.E.superba.1 <- median(RMT1.target[, Larvae[1]][RMT1.target[, Larvae[1]] > 0])
Target.SD.abundance.E.superba.1 <- sd(RMT1.target[, Larvae[1]][RMT1.target[, Larvae[1]] > 0])
Target.max.abundance.E.superba.1 <- max(RMT1.target[, Larvae[1]][RMT1.target[, Larvae[1]] > 0])
Target.min.abundance.E.superba.1 <- min(RMT1.target[, Larvae[1]][RMT1.target[, Larvae[1]] > 0])

## T. macrura
Target.Mean.abundance.T.macrura.1 <- mean(RMT1.target[, Larvae[2]][RMT1.target[, Larvae[2]] > 0])
Target.Median.abundance.T.macrura.1 <- median(RMT1.target[, Larvae[2]][RMT1.target[, Larvae[2]] > 0])
Target.SD.abundance.T.macrura.1 <- sd(RMT1.target[, Larvae[2]][RMT1.target[, Larvae[2]] > 0])
Target.max.abundance.T.macrura.1 <- max(RMT1.target[, Larvae[2]][RMT1.target[, Larvae[2]] > 0])
Target.min.abundance.T.macrura.1 <- min(RMT1.target[, Larvae[2]][RMT1.target[, Larvae[2]] > 0])

## Euphausiids
Target.Mean.abundance.Euphausiids <- mean(RMT1.target[, Larvae[3]][RMT1.target[, Larvae[3]] > 0])
Target.Median.abundance.Euphausiids <- median(RMT1.target[, Larvae[3]][RMT1.target[, Larvae[3]] > 0])
Target.SD.abundance.Euphausiids <- sd(RMT1.target[, Larvae[3]][RMT1.target[, Larvae[3]] > 0])
Target.max.abundance.Euphausiids <- max(RMT1.target[, Larvae[3]][RMT1.target[, Larvae[3]] > 0])
Target.min.abundance.Euphausiids <- min(RMT1.target[, Larvae[3]][RMT1.target[, Larvae[3]] > 0])

## Routine

## E.superba
Routine.Mean.abundance.E.superba.1 <- mean(RMT1.routine[, Larvae[1]][RMT1.routine[, Larvae[1]] > 0])
Routine.Median.abundance.E.superba.1 <- median(RMT1.routine[, Larvae[1]][RMT1.routine[, Larvae[1]] > 0])
Routine.SD.abundance.E.superba.1 <- sd(RMT1.routine[, Larvae[1]][RMT1.routine[, Larvae[1]] > 0])
Routine.max.abundance.E.superba.1 <- max(RMT1.routine[, Larvae[1]][RMT1.routine[, Larvae[1]] > 0])
Routine.min.abundance.E.superba.1 <- min(RMT1.routine[, Larvae[1]][RMT1.routine[, Larvae[1]] > 0])

## T. macrura
Routine.Mean.abundance.T.macrura.1 <- mean(RMT1.routine[, Larvae[2]][RMT1.routine[, Larvae[2]] > 0])
Routine.Median.abundance.T.macrura.1 <- median(RMT1.routine[, Larvae[2]][RMT1.routine[, Larvae[2]] > 0])
Routine.SD.abundance.T.macrura.1 <- sd(RMT1.routine[, Larvae[2]][RMT1.routine[, Larvae[2]] > 0])
Routine.max.abundance.T.macrura.1 <- max(RMT1.routine[, Larvae[2]][RMT1.routine[, Larvae[2]] > 0])
Routine.min.abundance.T.macrura.1 <- min(RMT1.routine[, Larvae[2]][RMT1.routine[, Larvae[2]] > 0])

## Euphausiids
Routine.Mean.abundance.Euphausiids <- mean(RMT1.routine[, Larvae[3]][RMT1.routine[, Larvae[3]] > 0])
Routine.Median.abundance.Euphausiids <- median(RMT1.routine[, Larvae[3]][RMT1.routine[, Larvae[3]] > 0])
Routine.SD.abundance.Euphausiids <- sd(RMT1.routine[, Larvae[3]][RMT1.routine[, Larvae[3]] > 0])
Routine.max.abundance.Euphausiids <- max(RMT1.routine[, Larvae[3]][RMT1.routine[, Larvae[3]] > 0])
Routine.min.abundance.Euphausiids <- min(RMT1.routine[, Larvae[3]][RMT1.routine[, Larvae[3]] > 0])

## Make a table:
RMT1.abundances <- data.frame(Species = c("Detections","Max", "Min", "Mean", "Median", "SD"),
                              `E. superba` = c(sprintf("%0.0f", Routine.RMT1.E.sup[2, 2]),
                                               sprintf("%0.2f", Routine.max.abundance.E.superba.1),
                                               sprintf("%0.2f", Routine.min.abundance.E.superba.1),
                                               sprintf("%0.2f", Routine.Mean.abundance.E.superba.1),
                                               sprintf("%0.2f", Routine.Median.abundance.E.superba.1),
                                               sprintf("%0.2f", Routine.SD.abundance.E.superba.1)),
                              `T. macrura` = c(sprintf("%0.0f", Routine.RMT1.T.mac[2, 2]),
                                               sprintf("%0.2f", Routine.max.abundance.T.macrura.1),
                                               sprintf("%0.2f", Routine.min.abundance.T.macrura.1),
                                               sprintf("%0.2f", Routine.Mean.abundance.T.macrura.1),
                                               sprintf("%0.2f", Routine.Median.abundance.T.macrura.1),
                                               sprintf("%0.2f", Routine.SD.abundance.T.macrura.1)),
                              Euphausiids = c(sprintf("%0.0f", Routine.RMT1.Eupha[2, 2]),
                                              sprintf("%0.2f", Routine.max.abundance.Euphausiids),
                                              sprintf("%0.2f", Routine.min.abundance.Euphausiids),
                                              sprintf("%0.2f", Routine.Mean.abundance.Euphausiids),
                                              sprintf("%0.2f", Routine.Median.abundance.Euphausiids),
                                              sprintf("%0.2f", Routine.SD.abundance.Euphausiids)),
                              `E. superba` = c(sprintf("%0.0f", Target.RMT1.E.sup[2, 2]),
                                               sprintf("%0.2f", Target.max.abundance.E.superba.1),
                                               sprintf("%0.2f", Target.min.abundance.E.superba.1),
                                               sprintf("%0.2f", Target.Mean.abundance.E.superba.1),
                                               sprintf("%0.2f", Target.Median.abundance.E.superba.1),
                                               sprintf("%0.2f", Target.SD.abundance.E.superba.1)),
                              `T. macrura` = c(sprintf("%0.0f", Target.RMT1.T.mac[2, 2]),
                                               sprintf("%0.2f", Target.max.abundance.T.macrura.1),
                                               sprintf("%0.2f", Target.min.abundance.T.macrura.1),
                                               sprintf("%0.2f", Target.Mean.abundance.T.macrura.1),
                                               sprintf("%0.2f", Target.Median.abundance.T.macrura.1),
                                               sprintf("%0.2f", Target.SD.abundance.T.macrura.1)),
                              Euphausiids = c(sprintf("%0.0f", Target.RMT1.Eupha[2, 2]),
                                              sprintf("%0.2f", Target.max.abundance.Euphausiids),
                                              sprintf("%0.2f", Target.min.abundance.Euphausiids),
                                              sprintf("%0.2f", Target.Mean.abundance.Euphausiids),
                                              sprintf("%0.2f", Target.Median.abundance.Euphausiids),
                                              sprintf("%0.2f", Target.SD.abundance.Euphausiids)))

## write.csv(RMT1.abundances, "RMT1.abundances.csv", row.names = FALSE)


```

## Compare to eDNA

### Figure 5E: compare RMT8, RMT1 and eDNA krill detections

```{r both-trawls-vs-eDNA}
trawl.columns.larvae <- c("E.superba.calyptopsis.I.tr", "E.superba.furcilia.II.tr",
                          "E.superba.furcilia.II.1.tr", "E.superba.late.stage.furcilia.tr",
                          "T.macrura.calyptopsis.I.tr", "T.macrura.calypopsis.II.tr",
                          "T.macrura.calyptopsis.III.tr", "T.macrura.late.furcilia.tr",
                          "T.macrura.furcilia.I.tr", "T.macrura.furcilia.II.tr",
                          "T.macrura.furcilia.III.tr", "T.macrura.furcilia.IV.tr",
                          "T.macrura.furcilia.V.tr", "T.macrura.furcilia.VI.tr",
                          "Euphausiid.calyptopsis.tr" , "Euphausiid.calyptopsis.I.tr",
                          "Euphausiid.calyptopsis.II.tr", "Euphausiid.furcilia.tr",
                          "Euphausiid.furcilia.I.tr")

trawls.eDNA <- subset(eDNA.CTDs, Sample %in% unique(c(RMT8$Sample, RMT1$Sample)))
trawls.eDNA$E.superba.larvae <- rowSums(trawls.eDNA[, trawl.columns.larvae[1:4]])
trawls.eDNA$T.macrura.larvae <- rowSums(trawls.eDNA[, trawl.columns.larvae[5:14]])
trawls.eDNA$Euphausiid.larvae <- rowSums(trawls.eDNA[, trawl.columns.larvae[15:19]])

## Subset where only stations that have both RMT1 AND RMT8 data are present are included
trawls.eDNA2 <- subset(trawls.eDNA, !is.na(E.superba.larvae) & !is.na(E.superba.estimate.tr))

## calculate values for euler diagram with overlap of eDNA detections with RMT1 AND RMT8, only for locations that have all three data streams collected:

trawls.eDNA2$Cop.Corr.R1[is.na(trawls.eDNA2$Cop.Corr.R1)] <- 0

eDNA.only2 <- length(trawls.eDNA2$Sample[trawls.eDNA2$E.superba.larvae == 0 & trawls.eDNA2$E.superba.estimate.tr == 0])
RMT1.only2 <- length(trawls.eDNA2$Sample[trawls.eDNA2$E.superba.larvae > 0 & trawls.eDNA2$E.superba.estimate.tr == 0 & trawls.eDNA2$Cop.Corr.R1 == 0])
RMT8.only2 <- length(trawls.eDNA2$Sample[trawls.eDNA2$E.superba.larvae == 0 & trawls.eDNA2$E.superba.estimate.tr > 0 & trawls.eDNA2$Cop.Corr.R1 == 0])
eDNA.RMT12 <- length(trawls.eDNA2$Sample[trawls.eDNA2$E.superba.larvae > 0 & trawls.eDNA2$E.superba.estimate.tr == 0 & trawls.eDNA2$Cop.Corr.R1 > 0])
eDNA.RMT82 <- length(trawls.eDNA2$Sample[trawls.eDNA2$E.superba.larvae == 0 & trawls.eDNA2$E.superba.estimate.tr > 0 & trawls.eDNA2$Cop.Corr.R1 > 0])
RMT1.RMT82  <- length(trawls.eDNA2$Sample[trawls.eDNA2$E.superba.larvae > 0 & trawls.eDNA2$E.superba.estimate.tr > 0 & trawls.eDNA2$Cop.Corr.R1 == 0])
eDNA.RMT8.RMT12 <- length(trawls.eDNA2$Sample[trawls.eDNA2$E.superba.larvae > 0 & trawls.eDNA2$E.superba.estimate.tr > 0 & trawls.eDNA2$Cop.Corr.R1 > 0])

Figure5E <- plot(euler(c(eDNA = eDNA.only2, RMT8 = RMT8.only2, RMT1 = RMT1.only2,
                         "eDNA&RMT8" = eDNA.RMT82, "eDNA&RMT1" = eDNA.RMT12, "RMT8&RMT1" = RMT1.RMT82,  "eDNA&RMT8&RMT1" = eDNA.RMT8.RMT12)),
                 quantities = TRUE, legend = TRUE, fills = list(fill = c("white", "olivedrab", "gold1"), alpha = 0.8))

```

### Figure5F: RMT8

```{r RMT8-vs-eDNA}
## RMT8: overlapping dataset with eDNA

RMT8.eDNA <- subset(RMT8, !is.na(RMT8$Sample))

Figure5F <- ggplot(RMT8.eDNA[!is.na(RMT8.eDNA$E.superba.estimate.tr) & RMT8.eDNA$E.superba.estimate.tr != 0, ],
                   aes(x = log(E.superba.estimate.tr), fill = class.strict, y = L1)) +
    geom_point(shape = 21, size = 3) +
    scale_fill_manual(values = c(age_manual_colours, "eDNA no krill" ="grey40")) +
    labs(x = "Log(RMT8 E. superba density)", y = "Log(copies, short marker)", fill = "eDNA age") +
    xlim(c(-2, 9)) + ylim(c(0, 8)) +
    theme_bw()

model.eDNA.trawl <- lm(log(E.superba.estimate.tr) ~ L1 + class.strict + trawltype.tr,
                       data = RMT8.eDNA[!is.na(RMT8.eDNA$E.superba.estimate.tr) & RMT8.eDNA$E.superba.estimate.tr != 0 , ])

plot(model.eDNA.trawl)
summary(model.eDNA.trawl)
anova(model.eDNA.trawl)

## Note: the relationship of eDNA quantity in relation to trawl density would be interesting to test - however, this would be most interesting at target trawl locations, i.e. where krill swarms were detected and sampled. There is very little overlap of target trawl locations and eDNA data (3 samples), so this cannot be tested here

```

### Figure 5G: RMT1

```{r RMT1-vs-eDNA}
## RMT1: overlapping dataset with eDNA

RMT1.eDNA <- subset(RMT1, !is.na(RMT1$Sample))

Figure5G <- ggplot(RMT1.eDNA[!is.na(RMT1.eDNA$E.superba.larvae) & RMT1.eDNA$E.superba.larvae != 0, ],
                   aes(x = log(E.superba.larvae), fill = class.strict, y = L1)) +
    geom_point(shape = 21, size = 3) +
    scale_fill_manual(values = c(age_manual_colours, "eDNA no krill" ="grey40")) +
    labs(x = "Log(RMT1 E. superba density)", y = "Log(copies, short marker)", fill = "eDNA age") +
    xlim(c(-2, 9)) + ylim(c(0, 8)) +
    theme_bw()

legend.5F <- get_legend(Figure5F)

Figure5FG.noleg <- plot_grid(Figure5F + theme(legend.position = "none"),
                             NULL,
                             Figure5G + theme(legend.position = "none"),
                             NULL,
                             ncol= 2, rel_widths = c(1, 0.1), labels = c("", "F", "", "G"))

Figure5FG <- plot_grid(Figure5FG.noleg, legend.5F, ncol = 2, rel_widths = c(1.1, 0.6))

```

### Assemble Figure 5

```{r assemble-fig-5}
Figure5EFG <- plot_grid(Figure5E, Figure5FG, nrow = 1, labels = c("E", ""), rel_widths = c(1, 1.7))

Figure5 <- plot_grid(Figure5ABCD, Figure5EFG, nrow = 2, rel_heights = c(2, 1))

## jpeg(filename = "Figure5.jpg", width = 4500, height = 4500, units = "px", quality = 100, res = 300)
if (save_figs) png(filename = "Figure5.png", width = 4500, height = 4500, res = 300)
print(Figure5)
if (save_figs) dev.off()

```


# Krill faecal pellet and moult sinking rates

```{r sinking-rates}
## faecal sinking rates:

## 27  1218 m d-1, median 304 m d1

## How long does it take to reach 3000 m depth?
## 27 m d-1:

poo.3000.slow <- 3000/27 ## 111 days
poo.3000.long <- 3000/1218 ## 2.46 days
poo.3000.median <- 3000/304 ## 9.87 days

## moult sinking rates:

## 0.06 to 1.18 cm s1, mean 0.78 cm s-1

moult.per.day.slow <- 0.06 / 100 * 60 * 60 * 24 ## 51.84 m d-1
moult.per.day.fast <- 1.18 / 100 * 60 * 60 * 24 ## 1019.52 m d-1
moult.per.day.mean <- 0.78 / 100 * 60 * 60 * 24 ## 673.92 m d-1

## Time to 3000 m depth
moult.3000.slow <- 3000 / moult.per.day.slow ## 57.87 days
moult.3000.long <- 3000 / moult.per.day.fast ## 2.94 days
moult.3000.mean <- 3000 / moult.per.day.mean ## 4.45 days

```
